---
title: "R00 Confounders Summary Stats"
author: "Ethan Walker"
date: "27 Feb 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 6)
```


```{r, message=FALSE}
library(tidyverse)
library(magrittr)
library(gridExtra)
library(lubridate)
library(haven)
library(knitr)
```

---

```{r}
#load full dataset
r00_full_joined_sphygmocor <- read_rds("output/r00_full_joined_sphygmocor.RDS")

r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")
```


```{r}
#Calculating and verifying method of categorizing waist/hip ratio
#WHR greater than or equal to 0.85 is counted as abdominal obesity
wthr_check <- r00_full_long %>% 
  select(whr, phase, house_id, assigned_stove, study_arm) %>% 
  filter(!is.na(assigned_stove)) %>% 
  filter(phase == 1) %>% 
  #split wthr at 0.85; >=0.85 = 1, <0.85 = 0
  mutate(wthr_cat = if_else(whr >= 0.85, 1, 0)) %>%
  group_by(study_arm) %>% 
  summarize(sum(wthr_cat, na.rm=TRUE))
```


# Secondary Stove Use
```{r}
sec_stove_stats <- r00_full_joined_sphygmocor %>% 
  select(aug_index, phase, days_sec, sec_stove, informed_consent) %>% 
  #na.exclude(days_sec) %>% 
  filter(phase == c(5,6)) 
table(sec_stove_stats$sec_stove)
```

# Pregnancies
## Current database says none reported across whole study?
```{r}
pregnancies <- r00_full_long %>% 
  select(study_arm, pregnant) %>% 
  mutate(pregnant = as.numeric(pregnant)) %>% 
  group_by(study_arm) %>% 
  summarise(sum(pregnant, na.rm=TRUE))
pregnancies
```

# ETS - environmental tobacco smoke and smoking past 6 months
## Current database says only 1 self-reported smoking in last 6 months
```{r}
smoke_summary <- r00_full_long %>% 
  select(study_arm, phase, smoke_6m, ets) %>% 
  na.exclude(study_arm) %>% 
  mutate(smoke_6m = as.numeric(smoke_6m), ets = as.numeric(ets)) %>% 
  group_by(phase, study_arm) %>% 
  summarise("n" = n(), 
            "Smoke last 6 months" = sum(smoke_6m, na.rm=TRUE), 
            "Report ETS" = sum(ets, na.rm=TRUE))
smoke_summary
```

# Summary stats for categorical confounders
## Phase 1 data
```{r}
cat_summary_stats <- r00_full_long %>% 
  select(phase, assigned_stove, school_bi, age_baseline,
         bmi, ses_materials, whr_cat, beds_new, dds_total, phys_act) %>% 
  filter(phase == 1) %>% 
  filter(!is.na(assigned_stove)) %>% 
  #split age at 40; >=40 = 1, <40 = 0
  mutate(age_cat_40 = if_else(age_baseline >= 40, 1, 0)) %>% 
  #split bmi at 26; >=26 = 1, <26 = 0
  mutate(bmi_cat_26 = if_else(bmi >= 26, 1, 0)) %>% 
  #split ses assets at 2; >2 = 1, <=2 = 0
  mutate(ses_cat_2 = if_else(ses_materials > 2, 1, 0)) %>% 
  mutate(whr_cat = if_else(whr_cat == "obese", 1, 0)) %>% 
  mutate(bpp_cat = if_else(beds_new >=0.5, 1, 0)) %>% 
  mutate(dds_cat = if_else(dds_total >=6, 1, 0)) %>% 
  mutate(phys_act_cat = if_else(phys_act >=300, 1, 0)) %>% 
  mutate(phase = as.factor(phase),
         school_bi = as.numeric(school_bi), 
         age_cat_40 = as.numeric(age_cat_40),
         bmi_cat_26 = as.numeric(bmi_cat_26),
         ses_cat_2 = as.numeric(ses_cat_2), 
         whr_cat = as.numeric(whr_cat),
         bpp_cat = as.numeric(bpp_cat),
         dds_cat = as.numeric(dds_cat),
         phys_act_cat = as.numeric(phys_act_cat)) %>%
  summarise("Total _(n)" = n(),
            "Total _(%)" = n()/n()*100,
            "6+ yrs school _(n)" = sum(school_bi, na.rm=TRUE),
            "6+ yrs school _(%)" = sum(school_bi, na.rm=TRUE)/n()*100,
            "40+ y/o _(n)" = sum(age_cat_40, na.rm=TRUE),
            "40+ y/o _(%)" = sum(age_cat_40, na.rm=TRUE)/n()*100,
            "26+ BMI _(n)" = sum(bmi_cat_26, na.rm=TRUE),
            "26+ BMI _(%)" = sum(bmi_cat_26, na.rm=TRUE)/n()*100,
            "WHR - Obese _(n)" = sum(whr_cat, na.rm=TRUE),
            "WHR - Obese _(%)" = sum(whr_cat, na.rm=TRUE)/n()*100,
            "3+ SES Assets _(n)" = sum(ses_cat_2, na.rm=TRUE),
            "3+ SES Assets _(%)" = sum(ses_cat_2, na.rm=TRUE)/n()*100,
            "0.5+ Bed/Person _(n)" = sum(bpp_cat, na.rm=TRUE),
            "0.5+ Bed/Person _(%)" = sum(bpp_cat, na.rm=TRUE)/n()*100,
            "6+ Diet Diversity _(n)" = sum(dds_cat, na.rm=TRUE),
            "6+ Diet Diversity _(%)" = sum(dds_cat, na.rm=TRUE)/n()*100,
            "300+ Phys Act _(n)" = sum(phys_act_cat, na.rm=TRUE),
            "300+ Phys Act _(%)" = sum(phys_act_cat, na.rm=TRUE)/n()*100) %>% 
  gather(Var, value) %>% 
  separate(Var, into = c("Variable", "stat"), sep = "_") %>% 
  spread(stat, value) %>% 
  arrange(desc(Variable)) %>% 
  select(Variable, "(n)", "(%)") %>% 
  rename("n" = "(n)", "%" = "(%)")
kable(cat_summary_stats, digits = 0)
```

# Summary stats for categorical confounders
## Grouped by study arm
## Phase 1 data
```{r}
cat_summary_stats <- r00_full_long %>% 
  select(phase, study_arm, assigned_stove, school_bi, age_baseline,
         bmi, ses_materials, whr_cat, beds_new, dds_total, phys_act) %>% 
  filter(phase == 1) %>% 
  filter(!is.na(assigned_stove)) %>% 
  #split age at 40; >=40 = 1, <40 = 0
  mutate(age_cat_40 = if_else(age_baseline >= 40, 1, 0)) %>% 
  #split bmi at 26; >=26 = 1, <26 = 0
  mutate(bmi_cat_26 = if_else(bmi >= 26, 1, 0)) %>% 
  #split ses assets at 2; >2 = 1, <=2 = 0
  mutate(ses_cat_2 = if_else(ses_materials > 2, 1, 0)) %>% 
  mutate(whr_cat = if_else(whr_cat == "obese", 1, 0)) %>% 
  mutate(bpp_cat = if_else(beds_new >=0.5, 1, 0)) %>% 
  mutate(dds_cat = if_else(dds_total >=6, 1, 0)) %>% 
  mutate(phys_act_cat = if_else(phys_act >=300, 1, 0)) %>% 
  mutate(phase = as.factor(phase),
         school_bi = as.numeric(school_bi), 
         age_cat_40 = as.numeric(age_cat_40),
         bmi_cat_26 = as.numeric(bmi_cat_26),
         ses_cat_2 = as.numeric(ses_cat_2), 
         whr_cat = as.numeric(whr_cat),
         bpp_cat = as.numeric(bpp_cat),
         dds_cat = as.numeric(dds_cat),
         phys_act_cat = as.numeric(phys_act_cat)) %>%
  group_by(study_arm) %>% 
  summarise("Total _(n)" = n(),
            "Total _(%)" = n()/n()*100,
            "6+ yrs school _(n)" = sum(school_bi, na.rm=TRUE),
            "6+ yrs school _(%)" = sum(school_bi, na.rm=TRUE)/n()*100,
            "40+ y/o _(n)" = sum(age_cat_40, na.rm=TRUE),
            "40+ y/o _(%)" = sum(age_cat_40, na.rm=TRUE)/n()*100,
            "26+ BMI _(n)" = sum(bmi_cat_26, na.rm=TRUE),
            "26+ BMI _(%)" = sum(bmi_cat_26, na.rm=TRUE)/n()*100,
            "WHR - Obese _(n)" = sum(whr_cat, na.rm=TRUE),
            "WHR - Obese _(%)" = sum(whr_cat, na.rm=TRUE)/n()*100,
            "3+ SES Assets _(n)" = sum(ses_cat_2, na.rm=TRUE),
            "3+ SES Assets _(%)" = sum(ses_cat_2, na.rm=TRUE)/n()*100,
            "0.5+ Bed/Person _(n)" = sum(bpp_cat, na.rm=TRUE),
            "0.5+ Bed/Person _(%)" = sum(bpp_cat, na.rm=TRUE)/n()*100,
            "6+ Diet Diversity _(n)" = sum(dds_cat, na.rm=TRUE),
            "6+ Diet Diversity _(%)" = sum(dds_cat, na.rm=TRUE)/n()*100,
            "300+ Phys Act _(n)" = sum(phys_act_cat, na.rm=TRUE),
            "300+ Phys Act _(%)" = sum(phys_act_cat, na.rm=TRUE)/n()*100) %>% 
  gather(Var, value, -study_arm) %>% 
  separate(Var, into = c("Variable", "stat"), sep = "_") %>% 
  spread(stat, value) %>% 
  arrange(desc(Variable), study_arm) %>% 
  select(study_arm, Variable, "(n)", "(%)") %>% 
  rename("Study Arm" = study_arm, "n" = "(n)", "%" = "(%)")
kable(cat_summary_stats, digits = 0)
```

## Grouped by phase
```{r}
cat_summary_stats <- r00_full_long %>% 
  filter(!is.na(assigned_stove)) %>% 
  select(house_id, phase, study_arm, aug_index, school_bi, age_baseline,
         bmi, ses_materials, whr_cat, beds_new, dds_total, phys_act) %>% 
  #split age at 40; >=40 = 1, <40 = 0
  mutate(age_cat_40 = if_else(age_baseline >= 40, 1, 0)) %>% 
  #split bmi at 26; >=26 = 1, <26 = 0
  mutate(bmi_cat_26 = if_else(bmi >= 26, 1, 0)) %>% 
  #split ses assets at 2; >2 = 1, <=2 = 0
  mutate(ses_cat_2 = if_else(ses_materials > 2, 1, 0)) %>% 
  mutate(whr_cat = if_else(whr_cat == "obese", 1, 0)) %>% 
  mutate(bpp_cat = if_else(beds_new >=0.5, 1, 0)) %>% 
  mutate(dds_cat = if_else(dds_total >=6, 1, 0)) %>% 
  mutate(phys_act_cat = if_else(phys_act >=300, 1, 0)) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         aug_index = as.numeric(aug_index),
         school_bi = as.numeric(school_bi), 
         age_cat_40 = as.numeric(age_cat_40),
         bmi_cat_26 = as.numeric(bmi_cat_26),
         ses_cat_2 = as.numeric(ses_cat_2), 
         whr_cat = as.numeric(whr_cat),
         bpp_cat = as.numeric(bpp_cat),
         dds_cat = as.numeric(dds_cat),
         phys_act_cat = as.numeric(phys_act_cat)) %>%
  group_by(phase) %>% 
  summarise("Total _(n)" = n(),
            "Total _(%)" = n()/n()*100,
            "6+ yrs school _(n)" = sum(school_bi, na.rm=TRUE),
            "6+ yrs school _(%)" = sum(school_bi, na.rm=TRUE)/n()*100,
            "40+ y/o _(n)" = sum(age_cat_40, na.rm=TRUE),
            "40+ y/o _(%)" = sum(age_cat_40, na.rm=TRUE)/n()*100,
            "26+ BMI _(n)" = sum(bmi_cat_26, na.rm=TRUE),
            "26+ BMI _(%)" = sum(bmi_cat_26, na.rm=TRUE)/n()*100,
            "WHR - Obese _(n)" = sum(whr_cat, na.rm=TRUE),
            "WHR - Obese _(%)" = sum(whr_cat, na.rm=TRUE)/n()*100, 
            "3+ SES Assets _(n)" = sum(ses_cat_2, na.rm=TRUE),
            "3+ SES Assets _(%)" = sum(ses_cat_2, na.rm=TRUE)/n()*100,
            "0.5+ Bed/Person _(n)" = sum(bpp_cat, na.rm=TRUE),
            "0.5+ Bed/Person _(%)" = sum(bpp_cat, na.rm=TRUE)/n()*100,
            "6+ Diet Diversity _(n)" = sum(dds_cat, na.rm=TRUE),
            "6+ Diet Diversity _(%)" = sum(dds_cat, na.rm=TRUE)/n()*100,
            "300+ Phys Act _(n)" = sum(phys_act_cat, na.rm=TRUE),
            "300+ Phys Act _(%)" = sum(phys_act_cat, na.rm=TRUE)/n()*100) %>% 
  gather(Var, value, -phase) %>% 
  separate(Var, into = c("Variable", "stat"), sep = "_") %>% 
  spread(stat, value) %>% 
  arrange(desc(Variable), phase) %>% 
  select(phase, Variable, "(n)", "(%)") %>% 
  rename("Phase" = phase, "n" = "(n)", "%" = "(%)")
kable(cat_summary_stats, digits = 0)
```

# Numeric summary stats for entire study population with Sphygmocor data
### Data from phase 1
```{r}
summary_stats <- r00_full_long %>% 
  select(house_id, phase, assigned_stove, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total, phys_act, school_self, whr, cook_years) %>% 
  filter(!is.na(assigned_stove)) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline),
         "Cook Years" = as.numeric(cook_years),
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight),
         "Waist/Hip Ratio" = as.numeric(whr), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total),
         "School - years" = as.numeric(school_self),
         "Phys Act" = as.numeric(phys_act)) %>% 
  filter(phase == 1) %>% 
  select(-house_id, -age_baseline, -height, -weight, -bmi, -ses_materials,
         -beds_new, -dds_total, -assigned_stove, -phys_act, - school_self, 
         -whr, -cook_years) %>%
  group_by(phase) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max), na.rm=TRUE) %>% 
  gather(var, value, -phase) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase) %>% 
  select(var, phase, mean, sd, min, median, max) %>% 
  rename("Variable" = var, "Phase" = phase)
kable(summary_stats, digits = 2)
```

# Numeric summary stats for entire study population with Sphygmocor data
### Data from phase 1
### Grouped by study arm
```{r}
summary_stats <- r00_full_long %>% 
  select(house_id, phase, assigned_stove, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total, phys_act, school_self, whr, study_arm, cook_years) %>% 
  filter(!is.na(assigned_stove)) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Cook Years" = as.numeric(cook_years),
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight),
         "Waist/Hip Ratio" = as.numeric(whr), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total),
         "School - years" = as.numeric(school_self),
         "Phys Act" = as.numeric(phys_act)) %>% 
  filter(phase == 1) %>% 
  select(-house_id, -age_baseline, -height, -weight, -bmi, -ses_materials,
         -beds_new, -dds_total, -assigned_stove, -phys_act, - school_self, 
         -whr, -cook_years) %>%
  group_by(phase, study_arm) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max), na.rm=TRUE) %>% 
  gather(var, value, -phase, -study_arm) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase, study_arm) %>% 
  select(var, phase, study_arm, mean, sd, min, median, max) %>% 
  rename("Variable" = var, "Phase" = phase, "Study Arm" = study_arm)
kable(summary_stats, digits = 2)
```

\pagebreak  

# Numeric summary stats grouped by study arm
### Data from phases 1 and 2
### Sphygmocor malfunction during phase 2
```{r}
summary_stats <- r00_full_joined_sphygmocor %>% 
  select(house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total, phys_act, school_self, whr, aug_index) %>% 
  na.exclude(aug_index) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "Waist/Hip Ratio" = as.numeric(whr), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total),
         "School - years" = as.numeric(school_self),
         "Phys Act" = as.numeric(phys_act)) %>% 
  filter(phase == 1 | phase == 2) %>% 
  select(-house_id, -age_baseline, -height, -weight, -bmi, -ses_materials,
         -beds_new, -dds_total, -aug_index, -phys_act, - school_self) %>%
  group_by(study_arm, phase) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max, "_n" = n())) %>% 
  gather(var, value, -study_arm, -phase) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase, study_arm) %>% 
  select(var, phase, study_arm, n, mean, sd, median, max, min) %>% 
  rename("Variable" = var, "Phase" = phase, "Study Arm" = study_arm)
kable(summary_stats, digits = 2)
```

\pagebreak  

# Boxplots
### Phase 1 data
```{r}
## BMI
# boxplots by study arm
confounder_boxplot <- r00_full_joined_sphygmocor %>% 
  select(study_arm, house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total) %>% 
  filter(phase == 1) %>% 
  na.exclude(bmi) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total)) %>%
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, `Body Mass Index`)) +
  ggtitle("BMI by Study Arm") +
  xlab("Study Arm") +
  ylab("BMI (kg/m^2)") +
  theme_bw()
confounder_boxplot
```

\pagebreak  

```{r}
## Age
# boxplots by study arm
confounder_boxplot <- r00_full_joined_sphygmocor %>% 
  select(study_arm, house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total) %>% 
  filter(phase == 1) %>% 
  na.exclude(age_baseline) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total)) %>%
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, `Baseline Age`)) +
  ggtitle("Age by Study Arm") +
  xlab("Study Arm") +
  ylab("Age (years)") +
  theme_bw()
confounder_boxplot
```

\pagebreak  

```{r}
## SES
# boxplots by study arm
confounder_boxplot <- r00_full_joined_sphygmocor %>% 
  select(study_arm, house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total) %>% 
  filter(phase == 1) %>% 
  na.exclude(ses_materials) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total)) %>%
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, `SES Materials`)) +
  ggtitle("SES Materials by Study Arm") +
  xlab("Study Arm") +
  ylab("SES Materials (n)") +
  theme_bw()
confounder_boxplot
```

\pagebreak  

```{r}
## Beds
# boxplots by study arm
confounder_boxplot <- r00_full_joined_sphygmocor %>% 
  select(study_arm, house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total) %>% 
  filter(phase == 1) %>% 
  na.exclude(beds_new) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total)) %>%
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, `Beds Per Person`)) +
  ggtitle("Beds Per Person by Study Arm") +
  xlab("Study Arm") +
  ylab("Beds Per Person") +
  theme_bw()
confounder_boxplot
```

\pagebreak  

```{r}
## DDS
# boxplots by study arm
confounder_boxplot <- r00_full_joined_sphygmocor %>% 
  select(study_arm, house_id, phase, age_baseline, height, weight, bmi, ses_materials,
         beds_new, dds_total) %>% 
  filter(phase == 1) %>% 
  na.exclude(dds_total) %>% 
  mutate("Baseline Age" = as.numeric(age_baseline), 
         "Height" = as.numeric(height), 
         "Weight" = as.numeric(weight), 
         "Body Mass Index" = as.numeric(bmi), 
         "SES Materials" = as.numeric(ses_materials), 
         "Beds Per Person" = as.numeric(beds_new), 
         "Dietary Diversity Score" = as.numeric(dds_total)) %>%
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, `Dietary Diversity Score`)) +
  ggtitle("Dietary Diversity Score by Study Arm") +
  xlab("Study Arm") +
  ylab("Dietary Diversity Score") +
  theme_bw()
confounder_boxplot
```


