---
title: "SUMs Summary Statistics"
author: "Ethan Walker"
date: "25 Feb 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 6)
```

```{r, message=FALSE}
library(tidyverse)
library(knitr)
```

```{r, message=FALSE}
r00_full_repeated_by_phase <- read_rds("output/r00_full_repeated_by_phase.rds")

sums_all_phases_clean <- read_rds("output/r00_sums_all_phases_clean.rds")

#r00_sums_full_dataset <- read_rds("output/r00_sums_full_dataset.rds")
```

# SUMs per phase
```{r}
sums_summary <- sums_all_phases_clean %>% 
  ungroup() %>% 
  select(house_id, phase, prim_or_sec) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         prim_or_sec = factor(prim_or_sec, levels = c("P", "S", "T", "Q"))) %>% 
  group_by(phase, prim_or_sec) %>% 
  summarise(n_distinct(house_id))
kable(sums_summary)
```

# Variables grouped by study arm
## Primary stoves
```{r}
summary_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = prim_sum_event_count_38, 
         "Events 40C" = prim_sum_event_count_40, 
         "Events 45C" = prim_sum_event_count_45, 
         "Events 50C" = prim_sum_event_count_50,
         "Mean event time 38C" = prim_sum_mean_event_time_38, 
         "Mean event time 40C" = prim_sum_mean_event_time_40, 
         "Mean event time 45C" = prim_sum_mean_event_time_45, 
         "Mean event time 50C" = prim_sum_mean_event_time_50,
         "Percent 38C" = prim_sum_temp_percent_38, 
         "Percent 40C" = prim_sum_temp_percent_40, 
         "Percent 45C" = prim_sum_temp_percent_45,
         "Percent 50C" = prim_sum_temp_percent_50) %>% 
  na.exclude("Events 38C") %>% 
  #filter(phase == 1 | phase == 2) %>% 
  group_by(study_arm, phase) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max, "_sums" = n(),
                     "_total" = sum)) %>% 
  gather(var, value, -study_arm, -phase) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase, study_arm) %>% 
  select(var, phase, study_arm, sums, total, mean, sd, min, median, max) %>% 
  mutate(mean = round(mean, digits = 2), 
         sd = round(sd, digits = 2), 
         median = round(median, digits = 2), 
         max = round(max, digits = 0), 
         min = round(min, digits = 0),
         total = round(total, digits = 0)) %>% 
  rename("Variable" = var, "Phase" = phase, "Study Arm" = study_arm, "Total SUMs" = sums) 
kable(summary_primary_stoves, digits = 2)
```

\pagebreak  

# Variables grouped by study arm
## Secondary stoves
```{r}
summary_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sec_sum_event_count_38, 
         "Events 40C" = sec_sum_event_count_40, 
         "Events 45C" = sec_sum_event_count_45, 
         "Events 50C" = sec_sum_event_count_50,
         "Mean event time 38C" = sec_sum_mean_event_time_38, 
         "Mean event time 40C" = sec_sum_mean_event_time_40, 
         "Mean event time 45C" = sec_sum_mean_event_time_45, 
         "Mean event time 50C" = sec_sum_mean_event_time_50,
         "Percent 38C" = sec_sum_temp_percent_38, 
         "Percent 40C" = sec_sum_temp_percent_40, 
         "Percent 45C" = sec_sum_temp_percent_45,
         "Percent 50C" = sec_sum_temp_percent_50) %>% 
  na.exclude("Events 38C") %>% 
  #filter(phase == 1 | phase == 2) %>% 
  group_by(study_arm, phase) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max, "_sums" = n(),
                     "_total" = sum)) %>% 
  gather(var, value, -study_arm, -phase) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase, study_arm) %>% 
  select(var, phase, study_arm, sums, total, mean, sd, min, median, max) %>% 
  mutate(mean = round(mean, digits = 2), 
         sd = round(sd, digits = 2), 
         median = round(median, digits = 2), 
         max = round(max, digits = 0), 
         min = round(min, digits = 0),
         total = round(total, digits = 0)) %>% 
  rename("Variable" = var, "Phase" = phase, "Study Arm" = study_arm, "Total SUMs" = sums) 
kable(summary_secondary_stoves, digits = 2)
```

\pagebreak  

# Histograms for frequency of measurements
## Number of events per household above specified temperature
## New event = > 1hr below specified temperature
## Primary Stoves
## SUMs data from 1083 household visits
```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = prim_sum_event_count_38, 
         "Events 40C" = prim_sum_event_count_40, 
         "Events 45C" = prim_sum_event_count_45, 
         "Events 50C" = prim_sum_event_count_50,
         "Mean event time 38C" = prim_sum_mean_event_time_38, 
         "Mean event time 40C" = prim_sum_mean_event_time_40, 
         "Mean event time 45C" = prim_sum_mean_event_time_45, 
         "Mean event time 50C" = prim_sum_mean_event_time_50,
         "Percent 38C" = prim_sum_temp_percent_38, 
         "Percent 40C" = prim_sum_temp_percent_40, 
         "Percent 45C" = prim_sum_temp_percent_45,
         "Percent 50C" = prim_sum_temp_percent_50) %>% 
  na.exclude("Events 38C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 38C`), bins = 8) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7), labels = c(0,1,2,3,4,5,6,7)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 38C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 38C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = prim_sum_event_count_38, 
         "Events 40C" = prim_sum_event_count_40, 
         "Events 45C" = prim_sum_event_count_45, 
         "Events 50C" = prim_sum_event_count_50,
         "Mean event time 38C" = prim_sum_mean_event_time_38, 
         "Mean event time 40C" = prim_sum_mean_event_time_40, 
         "Mean event time 45C" = prim_sum_mean_event_time_45, 
         "Mean event time 50C" = prim_sum_mean_event_time_50,
         "Percent 38C" = prim_sum_temp_percent_38, 
         "Percent 40C" = prim_sum_temp_percent_40, 
         "Percent 45C" = prim_sum_temp_percent_45,
         "Percent 50C" = prim_sum_temp_percent_50) %>% 
  na.exclude("Events 40C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 40C`), bins = 8) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7), labels = c(0,1,2,3,4,5,6,7)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 40C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 40C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = prim_sum_event_count_38, 
         "Events 40C" = prim_sum_event_count_40, 
         "Events 45C" = prim_sum_event_count_45, 
         "Events 50C" = prim_sum_event_count_50,
         "Mean event time 38C" = prim_sum_mean_event_time_38, 
         "Mean event time 40C" = prim_sum_mean_event_time_40, 
         "Mean event time 45C" = prim_sum_mean_event_time_45, 
         "Mean event time 50C" = prim_sum_mean_event_time_50,
         "Percent 38C" = prim_sum_temp_percent_38, 
         "Percent 40C" = prim_sum_temp_percent_40, 
         "Percent 45C" = prim_sum_temp_percent_45,
         "Percent 50C" = prim_sum_temp_percent_50) %>% 
  na.exclude("Events 45C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 45C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7), labels = c(0,1,2,3,4,5,6,7)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 45C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 45C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = prim_sum_event_count_38, 
         "Events 40C" = prim_sum_event_count_40, 
         "Events 45C" = prim_sum_event_count_45, 
         "Events 50C" = prim_sum_event_count_50,
         "Mean event time 38C" = prim_sum_mean_event_time_38, 
         "Mean event time 40C" = prim_sum_mean_event_time_40, 
         "Mean event time 45C" = prim_sum_mean_event_time_45, 
         "Mean event time 50C" = prim_sum_mean_event_time_50,
         "Percent 38C" = prim_sum_temp_percent_38, 
         "Percent 40C" = prim_sum_temp_percent_40, 
         "Percent 45C" = prim_sum_temp_percent_45,
         "Percent 50C" = prim_sum_temp_percent_50) %>% 
  na.exclude("Events 50C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 50C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7), labels = c(0,1,2,3,4,5,6,7)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 50C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 50C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

# Histograms for frequency of measurements
## Number of events per household above specified temperature
## New event = > 1hr below specified temperature
## Secondary Stoves
## SUMs data from 1088 household visits
```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sec_sum_event_count_38, 
         "Events 40C" = sec_sum_event_count_40, 
         "Events 45C" = sec_sum_event_count_45, 
         "Events 50C" = sec_sum_event_count_50,
         "Mean event time 38C" = sec_sum_mean_event_time_38, 
         "Mean event time 40C" = sec_sum_mean_event_time_40, 
         "Mean event time 45C" = sec_sum_mean_event_time_45, 
         "Mean event time 50C" = sec_sum_mean_event_time_50,
         "Percent 38C" = sec_sum_temp_percent_38, 
         "Percent 40C" = sec_sum_temp_percent_40, 
         "Percent 45C" = sec_sum_temp_percent_45,
         "Percent 50C" = sec_sum_temp_percent_50) %>% 
  na.exclude("Events 38C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 38C`), bins = 6) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6),
                       limits = c(1,6)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 38C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 38C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```

\pagebreak  

```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sec_sum_event_count_38, 
         "Events 40C" = sec_sum_event_count_40, 
         "Events 45C" = sec_sum_event_count_45, 
         "Events 50C" = sec_sum_event_count_50,
         "Mean event time 38C" = sec_sum_mean_event_time_38, 
         "Mean event time 40C" = sec_sum_mean_event_time_40, 
         "Mean event time 45C" = sec_sum_mean_event_time_45, 
         "Mean event time 50C" = sec_sum_mean_event_time_50,
         "Percent 38C" = sec_sum_temp_percent_38, 
         "Percent 40C" = sec_sum_temp_percent_40, 
         "Percent 45C" = sec_sum_temp_percent_45,
         "Percent 50C" = sec_sum_temp_percent_50) %>% 
  na.exclude("Events 40C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 40C`), bins = 6) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6),
                       limits = c(1,6)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 40C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 40C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```

\pagebreak  

```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sec_sum_event_count_38, 
         "Events 40C" = sec_sum_event_count_40, 
         "Events 45C" = sec_sum_event_count_45, 
         "Events 50C" = sec_sum_event_count_50,
         "Mean event time 38C" = sec_sum_mean_event_time_38, 
         "Mean event time 40C" = sec_sum_mean_event_time_40, 
         "Mean event time 45C" = sec_sum_mean_event_time_45, 
         "Mean event time 50C" = sec_sum_mean_event_time_50,
         "Percent 38C" = sec_sum_temp_percent_38, 
         "Percent 40C" = sec_sum_temp_percent_40, 
         "Percent 45C" = sec_sum_temp_percent_45,
         "Percent 50C" = sec_sum_temp_percent_50) %>% 
  na.exclude("Events 45C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 45C`), bins = 6) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6),
                       limits = c(1,6)) +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 45C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 45C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```

\pagebreak  

```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sec_sum_event_count_38, 
         "Events 40C" = sec_sum_event_count_40, 
         "Events 45C" = sec_sum_event_count_45, 
         "Events 50C" = sec_sum_event_count_50,
         "Mean event time 38C" = sec_sum_mean_event_time_38, 
         "Mean event time 40C" = sec_sum_mean_event_time_40, 
         "Mean event time 45C" = sec_sum_mean_event_time_45, 
         "Mean event time 50C" = sec_sum_mean_event_time_50,
         "Percent 38C" = sec_sum_temp_percent_38, 
         "Percent 40C" = sec_sum_temp_percent_40, 
         "Percent 45C" = sec_sum_temp_percent_45,
         "Percent 50C" = sec_sum_temp_percent_50) %>% 
  na.exclude("Events 50C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 50C`), bins = 6) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_x_continuous(breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6),
                       limits = c(1,6)) + 
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 50C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 50C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```