---
title: "R00 Dataset Cleaning and Additions"
author: "Ethan Walker"
date: "November 5, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
```

# This markdown begins with the long (repeated by phase/visit) version of the
# R00 dataset and makes further additions and cleaning adjustments
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds") 
```

# Bonnie made changes to long version of dataset - load that and save here
```{r}
r00_new_long <- read_csv("input/r00_full_dataset_31oct2019_by.csv")

r00_full_repeated_by_phase <- r00_new_long %>% 
  # removes 6 observations for participant who wasn't assigned to a study arm
  #filter(!is.na(study_arm)) %>% 
  mutate(assigned_stove = factor(assigned_stove, levels = c("Traditional", "Justa"))) %>% 
  mutate(stove_use_3 = factor(stove_use_3, 
                                levels = c("trad", "justa+trad", "justa/imprvd"))) 
```

# Add new/updated ambient temperature and pollution data
```{r}
ambient_temp_pollution <- read_rds("output/ambient_temp_pollution.rds")

new_data <- r00_full_long %>% 
  left_join(ambient_temp_pollution, by = c("house_id", "phase")) %>% 
  mutate(house_lat = house_lat.y,
         house_long = house_long.y,
         temp_datetime = temp_datetime.y,
         temp_c = temp_c.y,
         temp_lat = temp_lat.y,
         temp_long = temp_long.y,
         temp_rolling_24 = temp_rolling_24.y,
         ambient_pm = as.numeric(ambient_pm.y * 1000000000),
         ambient_bc = as.numeric(ambient_bc.y * 1000000000),
         ambient_oc = as.numeric(ambient_oc.y * 1000000000),
         pollution_lat = pollution_lat.y,
         pollution_long = pollution_long.y,
         pollution_datetime = pollution_datetime.y) %>% 
  select(-house_lat.y, -house_lat.x, -house_long.y, -house_long.x,
         -temp_datetime.y, -temp_datetime.x, -temp_c.y, -temp_c.x,
         -temp_lat.y, -temp_lat.x, -temp_long.y, -temp_long.x,
         -temp_rolling_24.y, -temp_rolling_24.x, -ambient_oc.y, -ambient_oc.x,
         -ambient_pm.y, -ambient_pm.x, -ambient_bc.y, -ambient_bc.x,
         -pollution_lat.y, -pollution_lat.x, -pollution_long.y, -pollution_long.x,
         -pollution_datetime.y, -pollution_datetime.x)
```

# Fix/re-order stove-use variables; they seemed to be ordered backwards after
# Bonnie made changes in SAS
```{r}
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")

new_data <- r00_full_long %>% 
  mutate(stove_use_4 = factor(stove_use_4,
                              levels = c("trad", "justa+trad", "justa+imp", "justa"),
                              labels = c("trad", "justa+trad", "justa+imp", "justa")),
         stove_use_days_stack = factor(stove_use_days_stack,
                  levels = c("trad", "justa+trad, 4+", "justa+trad, <4", "justa/imprvd"),
                  labels = c("trad", "justa+trad, 4+", "justa+trad, <4", "justa/imprvd")),
         stove_use_hours = factor(stove_use_hours,
                  levels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+",
                             "justa+trad, <3.5", "justa/imprvd, 3.5+", "justa/imprvd, <3.5"),
                  labels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+",
                        "justa+trad, <3.5", "justa/imprvd, 3.5+", "justa/imprvd, <3.5")))
```





################ DO THESE SAVING STEPS AFTER EACH DATA ADDITION, THEN LOAD TO SERVER
# Save final, combined dataset
```{r}
write_rds(new_data, "output/r00_full_repeated_by_phase.rds")

write_csv(new_data, "output/r00_full_repeated_by_phase.csv", na = " ")
```

# Change AIx/CPP outliers to NA and save dataset
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")

# USE THIS DATASET FOR AIx/CPP ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx
## This dataset is already saved -- use code above to load
r00_model_data_outliers_removed <- r00_full_long %>% 
  # removes 6 potential "outliers" with high or low AIx
  # removes 4 potential "outliers" > 75mmHg CPP
  mutate(aug_index = if_else(aug_index > 75 | aug_index < -25, 9999, aug_index)) %>% 
  mutate(pulse_pressure_central = if_else(pulse_pressure_central > 75,
                                          9999, pulse_pressure_central)) %>% 
  replace_with_na(replace = list(aug_index = 9999)) %>% 
  replace_with_na(replace = list(pulse_pressure_central = 9999)) 
write_rds(r00_model_data_outliers_removed, "output/r00_model_data_outliers_removed.rds")
```
