---
title: "Honduras R00 Models and Plots"
author: "Ethan Walker"
date: "18th Jan 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8, fig.height = 5)
```


```{r, include=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(pbkrtest)
library(emmeans)
library(broom)
library(purrr)
library(car)
library(forcats)
library(readxl)
library(naniar)
library(splines)
library(lubridate)
library(knitr)
library(influence.ME)
library(boxcoxmix)
jvPalette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
#load full dataset
r00_full_joined_sphygmocor <- read_rds("output/r00_full_joined_sphygmocor.RDS")
```


```{r}
## Data prep
r00_model_data <- r00_full_joined_sphygmocor %>% 
  mutate(sys_bp_central = as.numeric(sys_bp_central))%>% 
  mutate(dia_bp_central = as.numeric(dia_bp_central)) %>% 
  mutate(aug_index = as.numeric(aug_index)) %>% 
  mutate(aug_index_75 = as.numeric(aug_index_75)) %>% 
  mutate(pulse_pressure_periph = as.numeric(pulse_pressure_periph))%>% 
  mutate(pulse_pressure_central = as.numeric(pulse_pressure_central)) %>% 
  mutate(hr = as.numeric(hr)) %>% 
  mutate(bmi = as.numeric(bmi)) %>% 
  mutate(age_baseline = as.numeric(age_baseline)) %>% 
  mutate(phase = as.factor(phase)) %>%
  mutate(house_id = as.factor(house_id)) %>%
  #split age at 40; >40 = 1, <=40 = 0
  mutate(age_cat = if_else(age_baseline >= 40, ">=40", "<40")) %>% 
  mutate(age_cat = as.factor(age_cat)) %>% 
  #split bmi at 26; >26 = 1, <=26 = 0
  mutate(bmi_cat = if_else(bmi >= 26, ">=26", "<26")) %>% 
  mutate(bmi_cat = as.factor(bmi_cat)) %>%
  mutate(season = as.factor(season)) %>%
  mutate(assigned_stove = factor(assigned_stove, levels = c(0, 1), 
                                 labels = c("Traditional", "Justa"))) %>% 
  select(sys_bp_central, dia_bp_central, aug_index, aug_index_75, 
         hr, pulse_pressure_periph, season, 
         pulse_pressure_central, assigned_stove, house_id, age_cat, age_current, 
         age_baseline, bmi_cat, bmi, phase, study_arm, date_sphygmo) 

r00_model_data_6phases <- r00_model_data %>% 
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) == 6)

r00_model_data_outliers_aix <- r00_model_data %>% 
  # removes 6 potential "outliers" with high or low AIx
  filter(aug_index < 75 | is.na(aug_index)) %>% 
  filter(aug_index > -25 | is.na(aug_index))

r00_model_data_outliers_cpp <- r00_model_data %>% 
  # removes 42 potential "outliers" > 50mmHg CPP
  filter(pulse_pressure_central < 50 | is.na(pulse_pressure_central))

r00_model_data_baseline <- r00_model_data %>% 
  filter(phase == 1)
r00_model_data_p2 <- r00_model_data %>% 
  filter(phase == 2)
r00_model_data_p3 <- r00_model_data %>% 
  filter(phase == 3)
r00_model_data_p4 <- r00_model_data %>% 
  filter(phase == 4)
r00_model_data_p5 <- r00_model_data %>% 
  filter(phase == 5)
r00_model_data_p6 <- r00_model_data %>% 
  filter(phase == 6)
```

# Simple linear models between AIx and age/bmi
```{r}
#AIx
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_baseline)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p2)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p3)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p4)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p5)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p6)
tidy(aix_age)

aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_baseline)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p2)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p3)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p4)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p5)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p6)
tidy(aix_bmi)
```

\pagebreak  

# AIx analyses assessing Age and BMI as interaction terms
```{r}
## Model Summaries
## Honduras R00 Initial AIx Models
## Base model using season to account for time

sphygmo_model_season <- lmer(aug_index ~ assigned_stove + season + 
                          (1 | house_id), r00_model_data)
#  summary(sphygmo_model_season)

sphygmo_model_season_6phases <- lmer(aug_index ~ assigned_stove + season + 
                          (1 | house_id), r00_model_data_6phases)
#  summary(sphygmo_model_6phases)

sphygmo_model_season_outliers <- lmer(aug_index ~ assigned_stove + season + 
                          (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_season_outliers)

sphygmo_model_age <- lmer(aug_index ~ assigned_stove + age_baseline + season + 
                          (1 | house_id), r00_model_data)
#  summary(sphygmo_model_age)

sphygmo_model_age_int <- lmer(aug_index ~ assigned_stove*age_cat + season + 
                          (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_age_int)
age_int_emmeans <- emmeans(sphygmo_model_age_int, pairwise ~ assigned_stove | age_cat)
summary(age_int_emmeans)
plot(age_int_emmeans, comparisons = TRUE, xlab = "means", ylab = "assigned stove") 

sphygmo_model_bmi <- lmer(aug_index ~ assigned_stove + bmi + season + 
                          (1 | house_id), r00_model_data)
#  summary(sphygmo_model_bmi)

sphygmo_model_bmi_int <- lmer(aug_index ~ assigned_stove*bmi_cat + season + 
                          (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_bmi_int)
bmi_int_emmeans <- emmeans(sphygmo_model_bmi_int, pairwise ~ assigned_stove | bmi_cat)
summary(bmi_int_emmeans)
plot(bmi_int_emmeans, comparisons = TRUE, xlab = "means", ylab = "assigned stove")

## save model results
# write_rds(sphygmo_model_spline, "output/aix_model_17nov18.RDS")
```

\pagebreak  

# AIx Model Summaries and Plots
## Using season to account for time
## Sensitivity analyses with 6 outliers removed: 2 below -25 and 4 above 75
```{r}
tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "full dataset", "na")) 
tidy_sphygmo_model_season_6phases <- tidy(sphygmo_model_season_6phases, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "6 phases", "na")) 
tidy_sphygmo_model_season_outliers <- tidy(sphygmo_model_season_outliers, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "6 outliers removed", "na")) 

sphygmo_model_final_results <- rbind(tidy_sphygmo_model_season,
                                     tidy_sphygmo_model_season_6phases,
                                     tidy_sphygmo_model_season_outliers)
kable(sphygmo_model_final_results)


## Plot model estimates with age
plot_estimates <- sphygmo_model_final_results %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "AIx Models", 
          subtitle = "Full dataset vs sensitivity analyses") +
  labs(y = "Estimate (%): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

```{r}

## Format and plot models - age
tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "no age", "na")) 
tidy_sphygmo_model_age <- tidy(sphygmo_model_age, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "age", "na")) 

sphygmo_model_final_results_age <- rbind(tidy_sphygmo_model_season,
                                         tidy_sphygmo_model_age)
kable(sphygmo_model_final_results_age)


## Plot model estimates with age
plot_estimates <- sphygmo_model_final_results_age %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "AIx Models", subtitle = "Primary model vs model with age") +
  labs(y = "Estimate (%): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

```{r}

## Format and plot models - bmi
tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "no bmi", "na")) 
tidy_sphygmo_model_bmi <- tidy(sphygmo_model_bmi, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "bmi", "na")) 

sphygmo_model_final_results_bmi <- rbind(tidy_sphygmo_model_season,
                                         tidy_sphygmo_model_bmi)
kable(sphygmo_model_final_results_bmi)


## Plot model estimates with bmi
plot_estimates <- sphygmo_model_final_results_bmi %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "AIx Models", subtitle = "Primary model vs model with bmi") +
  labs(y = "Estimate (%): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

# AIx primary model diagnostic plots
```{r}
plot(sphygmo_model_season, main = "AIx primary model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(sphygmo_model_season), main = "AIx primary model QQ Plot")

plot(sphygmo_model_season_outliers, main = "AIx - 6 outliers removed", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(sphygmo_model_season_outliers), main = "AIx - 6 outliers removed QQ Plot")


#aix_influential <- influence(sphygmo_model_season, obs = TRUE)

#aix_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(aix_influential, which = "cook")
```

\pagebreak  


# Simple linear models between AIx and age/bmi
```{r}
#Central Pulse Pressure
cpp_age <- lm(pulse_pressure_central ~ age_baseline, data = r00_model_data_baseline)
tidy(cpp_age)

cpp_bmi <- lm(pulse_pressure_central ~ bmi, data = r00_model_data_baseline)
tidy(cpp_bmi)
```

\pagebreak  

# Central Pulse Pressure analyses assessing Age and BMI as interaction terms
```{r}
## Model Summaries
## Honduras R00 Initial Central Pulse Pressure Models ##

sphygmo_model_season <- lmer(pulse_pressure_central ~ assigned_stove + season +
                          (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_season)

sphygmo_model_season_6phases <- lmer(pulse_pressure_central ~ assigned_stove + season +
                          (1 | house_id), r00_model_data_6phases)
#  summary(sphygmo_model_season_6phases)

sphygmo_model_season_outliers <- lmer(pulse_pressure_central ~ assigned_stove + season + 
                          (1 | house_id), r00_model_data_outliers_cpp)
#  summary(sphygmo_model_season_outliers)

sphygmo_model_age <- lmer(pulse_pressure_central ~ assigned_stove + age_baseline + 
                          season +  (1 | house_id), r00_model_data)
#  summary(sphygmo_model_age)

sphygmo_model_age_int <- lmer(pulse_pressure_central ~ assigned_stove*age_cat + 
                              season + (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_age_int)
age_int_emmeans <- emmeans(sphygmo_model_age_int, pairwise ~ assigned_stove | age_cat)
summary(age_int_emmeans)
plot(age_int_emmeans, comparisons = TRUE, xlab = "means", ylab = "assigned stove")

sphygmo_model_bmi <- lmer(pulse_pressure_central ~ assigned_stove + bmi + 
                          season + (1 | house_id), r00_model_data)
#  summary(sphygmo_model_bmi)

sphygmo_model_bmi_int <- lmer(pulse_pressure_central ~ assigned_stove*bmi_cat + 
                              season + (1 | house_id), r00_model_data_outliers_aix)
#  summary(sphygmo_model_bmi_int)
bmi_int_emmeans <- emmeans(sphygmo_model_bmi_int, pairwise ~ assigned_stove | bmi_cat)
summary(bmi_int_emmeans)
plot(bmi_int_emmeans, comparisons = TRUE, xlab = "means", ylab = "assigned stove")

# save model results
# write_rds(sphygmo_model_spline, "output/aix_model_17nov18.RDS")
```

\pagebreak  

# Central Pulse Pressure Model Summaries and Plots
## Using season to account for time
## 6 AIx outliers removed from CPP dataset for analyses: n = 1380
```{r}

tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "full dataset", "na")) 
tidy_sphygmo_model_season_6phases <- tidy(sphygmo_model_season_6phases, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "6 phases", "na")) 
tidy_sphygmo_model_season_outliers <- tidy(sphygmo_model_season_outliers, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "42 CPP outliers removed", "na")) 

sphygmo_model_final_results <- rbind(tidy_sphygmo_model_season,
                                     tidy_sphygmo_model_season_6phases,
                                     tidy_sphygmo_model_season_outliers)
kable(sphygmo_model_final_results)


## Plot model estimates with age
plot_estimates <- sphygmo_model_final_results %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Central Pulse Pressure Models", 
          subtitle = "Full dataset vs sensitivity analyses") +
  labs(y = "Estimate (mmHg): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

```{r}

## Format and plot models - age
tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "no age", "na")) 
tidy_sphygmo_model_age <- tidy(sphygmo_model_age, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "age", "na")) 

sphygmo_model_final_results_age <- rbind(tidy_sphygmo_model_season,
                                         tidy_sphygmo_model_age)
kable(sphygmo_model_final_results_age)


## Plot model estimates with age
plot_estimates <- sphygmo_model_final_results_age %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Central Pulse Pressure", 
          subtitle = "Primary model vs model with age") +
  labs(y = "Estimate (mmHg): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

```{r}

## Format and plot models - bmi
tidy_sphygmo_model_season <- tidy(sphygmo_model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "no bmi", "na")) 
tidy_sphygmo_model_bmi <- tidy(sphygmo_model_bmi, conf.int = TRUE) %>% 
    filter(grepl('assigned', term)) %>% 
    rename(ci_low = conf.low, ci_hi = conf.high) %>% 
    mutate(model = if_else(term == "assigned_stoveJusta", "bmi", "na")) 

sphygmo_model_final_results_bmi <- rbind(tidy_sphygmo_model_season,
                                         tidy_sphygmo_model_bmi)
kable(sphygmo_model_final_results_bmi)


## Plot model estimates with bmi
plot_estimates <- sphygmo_model_final_results_bmi %>%
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=ci_low, ymax=ci_hi), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Central Pulse Pressure", 
          subtitle = "Primary model vs model with bmi") +
  labs(y = "Estimate (mmHg): Justa vs Traditional") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 15, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

# Central Pulse Pressure primary model diagnostic plots
```{r}
plot(sphygmo_model_season, main = "Central Pulse Pressure primary model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(sphygmo_model_season), main = "Central Pulse Pressure primary model QQ Plot")

plot(sphygmo_model_season_outliers, 
     main = "Central Pulse Pressure - 42 CPP outliers removed", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(sphygmo_model_season_outliers), 
       main = "Central Pulse Pressure - 42 CPP outliers removed QQ Plot")


#cpp_influential <- influence(sphygmo_model_season, obs = TRUE)

#cpp_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(cpp_influential, which = "cook")
```

