---
title: "SUMs Data Cleaning"
author: "Ethan Walker"
date: "12 March 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(lubridate)
library(caTools)
library(knitr)
```

# Load datasets
```{r, message=FALSE}
exposure_times <- read_csv("input/honduras_r00_exposure_times_all_phases.csv")

sums_all_phases_full <- read_rds("output/r00_sums_all_phases_full.rds")

sums_all_phases_clean <- read_rds("output/r00_sums_all_phases_clean.rds")

r00_full_repeated_by_phase <- read_rds("output/r00_full_repeated_by_phase.rds")
```

#Prep Exposure Times
```{r}
exposure_times_clean <- exposure_times %>% 
  unite(setup_datetime, c(setup_date, setup_time), sep = " ") %>% 
  mutate(setup_datetime = mdy_hms(setup_datetime)) %>%
  unite(takedown_datetime, c(takedown_date, takedown_time), sep = " ") %>% 
  mutate(takedown_datetime = mdy_hms(takedown_datetime)) 

#17 occurrences with no date or time for setup or takedown
```

#Read in SUMs files
```{r}
#Phase 1
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 1 - Aug-Dec 2015/SUMs")

#This pulls in all CSVs, skipping the first 19 rows of description, and binds all data together
phase_1_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
#This creates a column of the row name (file name) to be used later for labeling
phase_1_data$mycolumn <- substring(row.names(phase_1_data),1,10)


#Phase 2
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 2 - Jan-May 2016/SUMs")

phase_2_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
phase_2_data$mycolumn <- substring(row.names(phase_2_data),1,10)


#Phase 3
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 3 - Sep-Dec 2016/SUMs")

phase_3_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
phase_3_data$mycolumn <- substring(row.names(phase_3_data),1,10)


#Phase 4
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 4 - Feb-May 2017/SUMs")

phase_4_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
phase_4_data$mycolumn <- substring(row.names(phase_4_data),1,10)


#Phase 5
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 5 - Aug-Dec 2017/SUMs")

phase_5_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
phase_5_data$mycolumn <- substring(row.names(phase_5_data),1,10)


#Phase 6
setwd("T:/Rsch-Clark/Honduras Cookstove Projects/Data/Data R00/original data/Phase 6 - Feb-May 2018/SUMs")

phase_6_data <- do.call("rbind", sapply(list.files(pattern = ".csv$", full.names = TRUE), 
                                     read_csv, col_names = TRUE, col_types = cols(), 
                                     skip = 19, simplify = FALSE)) 
phase_6_data$mycolumn <- substring(row.names(phase_6_data),1,10)
```

#Clean SUMs files
```{r}
#Remove row names
rownames(phase_1_data) <- c()
phase_1_data_clean <- phase_1_data %>% 
  #pull out house_id and primary vs secondary stove, remove unnecessary info
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  #separate into 2 variables
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 

rownames(phase_2_data) <- c()
phase_2_data_clean <- phase_2_data %>% 
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 

rownames(phase_3_data) <- c()
phase_3_data_clean <- phase_3_data %>% 
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 

rownames(phase_4_data) <- c()
phase_4_data_clean <- phase_4_data %>% 
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 

rownames(phase_5_data) <- c()
phase_5_data_clean <- phase_5_data %>% 
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 

rownames(phase_6_data) <- c()
phase_6_data_clean <- phase_6_data %>% 
  separate(mycolumn, c("trash", "house_id"), sep = "./") %>% 
  separate(house_id, c("house_id", "prim_or_sec"), sep = "_") %>% 
  rename(datetime = `Date/Time`, temp = Value) %>% 
  select(-Unit, - trash) %>% 
  mutate(exposure_datetime = mdy_hms(datetime)) 
```

#Select for specified exposure times and add vars for specific temp thresholds
```{r}
phase_1_data_full <- exposure_times_clean %>% 
  full_join(phase_1_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  # new variable indicating if exposure time is between setup and takedown times
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  # filter for times when exposure time is between setup and takedown times
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  # new variables saying if temp meets a threshold at each sums datapoint
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))

phase_2_data_full <- exposure_times_clean %>% 
  full_join(phase_2_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))

phase_3_data_full <- exposure_times_clean %>% 
  full_join(phase_3_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))

phase_4_data_full <- exposure_times_clean %>% 
  full_join(phase_4_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))

phase_5_data_full <- exposure_times_clean %>% 
  full_join(phase_5_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))

phase_6_data_full <- exposure_times_clean %>% 
  full_join(phase_6_data_clean, by = c("house_id")) %>% 
  group_by(house_id) %>% 
  mutate(logic_datetime = if_else((exposure_datetime > setup_datetime) & 
                              (exposure_datetime < takedown_datetime), 
                              "keep", "trash")) %>% 
  filter(logic_datetime == "keep") %>% 
  select(-datetime) %>% 
  mutate(temp_35 = if_else(temp >= 35, TRUE, FALSE)) %>% 
  mutate(temp_38 = if_else(temp >= 38, TRUE, FALSE)) %>% 
  mutate(temp_40 = if_else(temp >= 40, TRUE, FALSE)) %>% 
  mutate(temp_45 = if_else(temp >= 45, TRUE, FALSE)) %>% 
  mutate(temp_50 = if_else(temp >= 50, TRUE, FALSE))
```

#Save data by individual phase
```{r}
write_rds(phase_1_data_full, "output/r00_phase_1_sums_data.rds")
write_csv(phase_1_data_full, "output/r00_phase_1_sums_data.csv")

write_rds(phase_2_data_full, "output/r00_phase_2_sums_data.rds")
write_csv(phase_2_data_full, "output/r00_phase_2_sums_data.csv")

write_rds(phase_3_data_full, "output/r00_phase_3_sums_data.rds")
write_csv(phase_3_data_full, "output/r00_phase_3_sums_data.csv")

write_rds(phase_4_data_full, "output/r00_phase_4_sums_data.rds")
write_csv(phase_4_data_full, "output/r00_phase_4_sums_data.csv")

write_rds(phase_5_data_full, "output/r00_phase_5_sums_data.rds")
write_csv(phase_5_data_full, "output/r00_phase_5_sums_data.csv")

write_rds(phase_6_data_full, "output/r00_phase_6_sums_data.rds")
write_csv(phase_6_data_full, "output/r00_phase_6_sums_data.csv")
```

#Analyze datasets and create final variables
```{r}
#Combine data from all phases into single dataset
sums_all_phases_full <- rbind(phase_1_data_full, phase_2_data_full, phase_3_data_full, 
                             phase_4_data_full, phase_5_data_full, phase_6_data_full)

write_rds(sums_all_phases_full, "output/r00_sums_all_phases_full.rds")
write_csv(sums_all_phases_full, "output/r00_sums_all_phases_full.csv")
```

```{r}
sums_all_phases_clean <- sums_all_phases_full %>% 
  #relabel temp vars: 1=true, 0=false
  mutate(temp_35 = if_else(temp_35 == TRUE, 1, 0)) %>%
  mutate(temp_38 = if_else(temp_38 == TRUE, 1, 0)) %>%
  mutate(temp_40 = if_else(temp_40 == TRUE, 1, 0)) %>%
  mutate(temp_45 = if_else(temp_45 == TRUE, 1, 0)) %>%
  mutate(temp_50 = if_else(temp_50 == TRUE, 1, 0)) %>% 
  group_by(house_id, phase, prim_or_sec) %>% 
  #create percent usage vars
  mutate(temp_35_percent = mean(temp_35)) %>% 
  mutate(temp_38_percent = mean(temp_38)) %>%
  mutate(temp_40_percent = mean(temp_40)) %>%
  mutate(temp_45_percent = mean(temp_45)) %>%
  mutate(temp_50_percent = mean(temp_50))

write_rds(sums_all_phases_clean, "output/r00_sums_all_phases_clean.rds")
write_csv(sums_all_phases_clean, "output/r00_sums_all_phases_clean.csv")

sums_summary <- sums_all_phases_clean %>% 
  ungroup() %>% 
  select(house_id, phase, prim_or_sec) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         prim_or_sec = factor(prim_or_sec, levels = c("P", "S", "T", "Q"))) %>% 
  group_by(phase, prim_or_sec) %>% 
  summarise(n_distinct(house_id))
sums_summary
```

# create new vars for events of temp > 38 - primary stoves
```{r}
sums_temp38_clean <- sums_all_phases_clean %>% 
  # filter for primary stoves only
  filter(prim_or_sec == "P") %>% 
  group_by(house_id, phase) %>%
  # filter for 38 degree temp threshold
  filter(temp_38 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 38+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_38_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_38_new_event = if_else(lead(temp_38_new_event) == 2, 3, temp_38_new_event)) %>% 
  mutate(temp_38_new_event = if_else(is.na(time_diff), 1, temp_38_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_38_new_event = if_else(lead(temp_38_new_event) == 1, 3, temp_38_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_38_new_event == 1 | temp_38_new_event == 2 | temp_38_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal - 1=start, 3=end
  mutate(temp_38_event_time = if_else(temp_38_new_event == 2, 1, temp_38_new_event)) %>% 
  spread(temp_38_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_38 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_38)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_38 = n_distinct(event_time_38)) %>% 
  select(house_id, phase, temp_38_percent, event_time_38, event_count_38) %>% 
  # calc mean event time per household, per phase
  mutate(prim_sum_mean_event_time_38 = mean(event_time_38)) %>% 
  rename(prim_sum_temp_percent_38 = temp_38_percent,
         prim_sum_event_count_38 = event_count_38) %>% 
  select(-event_time_38) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(prim_sum_event_count_38, .keep_all = TRUE)
  
write_rds(sums_temp38_clean, "output/r00_sums_temp38_clean.rds")
write_csv(sums_temp38_clean, "output/r00_sums_temp38_clean.csv")
```

# create new vars for events of temp > 40 - primary stoves
```{r}
sums_temp40_clean <- sums_all_phases_clean %>% 
  # filter for primary stoves only
  filter(prim_or_sec == "P") %>% 
  group_by(house_id, phase) %>%
  # filter for 40 degree temp threshold
  filter(temp_40 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 40+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_40_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_40_new_event = if_else(lead(temp_40_new_event) == 2, 3, temp_40_new_event)) %>% 
  mutate(temp_40_new_event = if_else(is.na(time_diff), 1, temp_40_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_40_new_event = if_else(lead(temp_40_new_event) == 1, 3, temp_40_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_40_new_event == 1 | temp_40_new_event == 2 | temp_40_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_40_event_time = if_else(temp_40_new_event == 2, 1, temp_40_new_event)) %>% 
  spread(temp_40_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_40 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_40)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_40 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_40_percent, event_time_40, event_count_40) %>% 
  # calc mean event time per household, per phase
  mutate(prim_sum_mean_event_time_40 = mean(event_time_40)) %>% 
  rename(prim_sum_temp_percent_40 = temp_40_percent,
         prim_sum_event_count_40 = event_count_40) %>% 
  select(-event_time_40) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(prim_sum_event_count_40, .keep_all = TRUE)
  
write_rds(sums_temp40_clean, "output/r00_sums_temp40_clean.rds")
write_csv(sums_temp40_clean, "output/r00_sums_temp40_clean.csv")
```

# create new vars for events of temp > 45 - primary stoves
```{r}
sums_temp45_clean <- sums_all_phases_clean %>% 
  # filter for primary stoves only
  filter(prim_or_sec == "P") %>% 
  group_by(house_id, phase) %>%
  # filter for 45 degree temp threshold
  filter(temp_45 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 45+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_45_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_45_new_event = if_else(lead(temp_45_new_event) == 2, 3, temp_45_new_event)) %>% 
  mutate(temp_45_new_event = if_else(is.na(time_diff), 1, temp_45_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_45_new_event = if_else(lead(temp_45_new_event) == 1, 3, temp_45_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_45_new_event == 1 | temp_45_new_event == 2 | temp_45_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_45_event_time = if_else(temp_45_new_event == 2, 1, temp_45_new_event)) %>% 
  spread(temp_45_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_45 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_45)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_45 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_45_percent, event_time_45, event_count_45) %>% 
  # calc mean event time per household, per phase
  mutate(prim_sum_mean_event_time_45 = mean(event_time_45)) %>% 
  rename(prim_sum_temp_percent_45 = temp_45_percent,
         prim_sum_event_count_45 = event_count_45) %>% 
  select(-event_time_45) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(prim_sum_event_count_45, .keep_all = TRUE)
  
write_rds(sums_temp45_clean, "output/r00_sums_temp45_clean.rds")
write_csv(sums_temp45_clean, "output/r00_sums_temp45_clean.csv")
```

# create new vars for events of temp > 50 - primary stoves
```{r}
sums_temp50_clean <- sums_all_phases_clean %>% 
  # filter for primary stoves only
  filter(prim_or_sec == "P") %>% 
  group_by(house_id, phase) %>%
  # filter for 50 degree temp threshold
  filter(temp_50 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 50+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_50_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_50_new_event = if_else(lead(temp_50_new_event) == 2, 3, temp_50_new_event)) %>% 
  mutate(temp_50_new_event = if_else(is.na(time_diff), 1, temp_50_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_50_new_event = if_else(lead(temp_50_new_event) == 1, 3, temp_50_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_50_new_event == 1 | temp_50_new_event == 2 | temp_50_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_50_event_time = if_else(temp_50_new_event == 2, 1, temp_50_new_event)) %>% 
  spread(temp_50_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_50 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_50)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_50 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_50_percent, event_time_50, event_count_50) %>% 
  # calc mean event time per household, per phase
  mutate(prim_sum_mean_event_time_50 = mean(event_time_50)) %>% 
  rename(prim_sum_temp_percent_50 = temp_50_percent,
         prim_sum_event_count_50 = event_count_50) %>% 
  select(-event_time_50) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(prim_sum_event_count_50, .keep_all = TRUE)
  
write_rds(sums_temp50_clean, "output/r00_sums_temp50_clean.rds")
write_csv(sums_temp50_clean, "output/r00_sums_temp50_clean.csv")
```


# create new vars for events of temp > 38 - secondary stoves
```{r}
sums_temp38_secondary_clean <- sums_all_phases_clean %>% 
  # filter for secondary stoves only
  filter(prim_or_sec %in% c("S", "T", "Q")) %>% 
  group_by(house_id, phase) %>%
  # filter for 38 degree temp threshold
  filter(temp_38 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 38+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_38_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_38_new_event = if_else(lead(temp_38_new_event) == 2, 3, temp_38_new_event)) %>% 
  mutate(temp_38_new_event = if_else(is.na(time_diff), 1, temp_38_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_38_new_event = if_else(lead(temp_38_new_event) == 1, 3, temp_38_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_38_new_event == 1 | temp_38_new_event == 2 | temp_38_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_38_event_time = if_else(temp_38_new_event == 2, 1, temp_38_new_event)) %>% 
  spread(temp_38_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_38 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_38)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_38 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_38_percent, event_time_38, event_count_38) %>% 
  # calc mean event time per household, per phase
  mutate(sec_sum_mean_event_time_38 = mean(event_time_38)) %>% 
  rename(sec_sum_temp_percent_38 = temp_38_percent,
         sec_sum_event_count_38 = event_count_38) %>% 
  select(-event_time_38) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(sec_sum_event_count_38, .keep_all = TRUE)
  
write_rds(sums_temp38_secondary_clean, "output/sums_temp38_secondary_clean.rds")
write_csv(sums_temp38_secondary_clean, "output/sums_temp38_secondary_clean.csv")
```

# create new vars for events of temp > 40 - secondary stoves
```{r}
sums_temp40_secondary_clean <- sums_all_phases_clean %>% 
  # filter for secondary stoves only
  filter(prim_or_sec %in% c("S", "T", "Q")) %>% 
  group_by(house_id, phase) %>%
  # filter for 40 degree temp threshold
  filter(temp_40 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 40+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_40_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_40_new_event = if_else(lead(temp_40_new_event) == 2, 3, temp_40_new_event)) %>% 
  mutate(temp_40_new_event = if_else(is.na(time_diff), 1, temp_40_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_40_new_event = if_else(lead(temp_40_new_event) == 1, 3, temp_40_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_40_new_event == 1 | temp_40_new_event == 2 | temp_40_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_40_event_time = if_else(temp_40_new_event == 2, 1, temp_40_new_event)) %>% 
  spread(temp_40_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_40 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_40)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_40 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_40_percent, event_time_40, event_count_40) %>% 
  # calc mean event time per household, per phase
  mutate(sec_sum_mean_event_time_40 = mean(event_time_40)) %>% 
  rename(sec_sum_temp_percent_40 = temp_40_percent,
         sec_sum_event_count_40 = event_count_40) %>% 
  select(-event_time_40) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(sec_sum_event_count_40, .keep_all = TRUE)
  
write_rds(sums_temp40_secondary_clean, "output/sums_temp40_secondary_clean.rds")
write_csv(sums_temp40_secondary_clean, "output/sums_temp40_secondary_clean.csv")
```

# create new vars for events of temp > 45 - secondary stoves
```{r}
sums_temp45_secondary_clean <- sums_all_phases_clean %>% 
  # filter for secondary stoves only
  filter(prim_or_sec %in% c("S", "T", "Q")) %>% 
  group_by(house_id, phase) %>%
  # filter for 45 degree temp threshold
  filter(temp_45 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 45+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_45_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_45_new_event = if_else(lead(temp_45_new_event) == 2, 3, temp_45_new_event)) %>% 
  mutate(temp_45_new_event = if_else(is.na(time_diff), 1, temp_45_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_45_new_event = if_else(lead(temp_45_new_event) == 1, 3, temp_45_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_45_new_event == 1 | temp_45_new_event == 2 | temp_45_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_45_event_time = if_else(temp_45_new_event == 2, 1, temp_45_new_event)) %>% 
  spread(temp_45_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_45 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_45)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_45 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_45_percent, event_time_45, event_count_45) %>% 
  # calc mean event time per household, per phase
  mutate(sec_sum_mean_event_time_45 = mean(event_time_45)) %>% 
  rename(sec_sum_temp_percent_45 = temp_45_percent,
         sec_sum_event_count_45 = event_count_45) %>% 
  select(-event_time_45) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(sec_sum_event_count_45, .keep_all = TRUE)
  
write_rds(sums_temp45_secondary_clean, "output/sums_temp45_secondary_clean.rds")
write_csv(sums_temp45_secondary_clean, "output/sums_temp45_secondary_clean.csv")
```

# create new vars for events of temp > 50 - secondary stoves
```{r}
sums_temp50_secondary_clean <- sums_all_phases_clean %>% 
  # filter for secondary stoves only
  filter(prim_or_sec %in% c("S", "T", "Q")) %>% 
  group_by(house_id, phase) %>%
  # filter for 50 degree temp threshold
  filter(temp_50 == 1) %>% 
  mutate(exposure_datetime_lag = lag(exposure_datetime)) %>% 
  # calc time difference between each datapoint that was 50+ temperature
  mutate(time_diff = exposure_datetime - exposure_datetime_lag) %>% 
  # first event of recording session = 1, new event (>1hr apart) = 2, end event = 3
  mutate(temp_50_new_event = if_else(time_diff>3600, 2, 0)) %>% 
  mutate(temp_50_new_event = if_else(lead(temp_50_new_event) == 2, 3, temp_50_new_event)) %>% 
  mutate(temp_50_new_event = if_else(is.na(time_diff), 1, temp_50_new_event)) %>% 
  ungroup() %>% 
  mutate(temp_50_new_event = if_else(lead(temp_50_new_event) == 1, 3, temp_50_new_event)) %>% 
  # keep only times when events began or ended
  filter(temp_50_new_event == 1 | temp_50_new_event == 2 | temp_50_new_event ==3) %>% 
  group_by(house_id, phase) %>% 
  # new events and first events now equal
  mutate(temp_50_event_time = if_else(temp_50_new_event == 2, 1, temp_50_new_event)) %>% 
  spread(temp_50_event_time, exposure_datetime) %>% 
  mutate(event_start = `1`, event_end = `3`) %>% 
  mutate(event_end = lead(event_end)) %>% 
  # convert event time to minutes
  mutate(event_time_50 = (event_end - event_start)/60) %>% 
  filter(!is.na(event_time_50)) %>% 
  # new event count var
  group_by(house_id, phase) %>% 
  mutate(event_count_50 = n_distinct(event_start)) %>% 
  select(house_id, phase, temp_50_percent, event_time_50, event_count_50) %>% 
  # calc mean event time per household, per phase
  group_by(house_id, phase) %>% 
  mutate(sec_sum_mean_event_time_50 = mean(event_time_50)) %>% 
  rename(sec_sum_temp_percent_50 = temp_50_percent,
         sec_sum_event_count_50 = event_count_50) %>% 
  select(-event_time_50) %>% 
  # keep only one row of distinct values per household, per phase
  distinct(sec_sum_event_count_50, .keep_all = TRUE)
  
write_rds(sums_temp50_secondary_clean, "output/sums_temp50_secondary_clean.rds")
write_csv(sums_temp50_secondary_clean, "output/sums_temp50_secondary_clean.csv")
```

# Combine clean SUMs datasets
```{r}
r00_sums_full_dataset <- sums_temp38_clean %>% 
  full_join(sums_temp40_clean, by = c("house_id", "phase")) %>% 
  full_join(sums_temp45_clean, by = c("house_id", "phase")) %>% 
  full_join(sums_temp50_clean, by = c("house_id", "phase")) %>% 
  full_join(sums_temp38_secondary_clean, by = c("house_id", "phase")) %>%
  full_join(sums_temp40_secondary_clean, by = c("house_id", "phase")) %>%
  full_join(sums_temp45_secondary_clean, by = c("house_id", "phase")) %>% 
  full_join(sums_temp50_secondary_clean, by = c("house_id", "phase")) %>% 
  ungroup() %>% 
  mutate(phase = as.factor(phase))

# replace na values with 0
r00_sums_full_dataset[is.na(r00_sums_full_dataset)] <- 0
```

# Save final SUMs dataset
###### Join with full dataset and save using "r00_initial_data_cleaning.rmd"
```{r}
write_rds(r00_sums_full_dataset, "output/r00_sums_full_dataset.rds")
write_csv(r00_sums_full_dataset, "output/r00_sums_full_dataset.csv")
```

## Testing new 'sumsarizer' package: install_github("geocene/sumsarizer")
### How-to vignette: https://github.com/Geocene/sumsarizer/blob/master/vignettes/how-to.Rmd
```{r}
library(sumsarizer)
library(knitr)

# load a single sums data file
test_file <- import_sums("input/sums/ANT011_Primary_51541_26Oct2016.csv")

# detect an event at a set threshold
test_detector <- apply_detector(test_file, threshold_detector, threshold=35, direction=">")


test_firefinder <- apply_detector(test_file, firefinder_detector)


test_events <- list_events(test_firefinder)


kable(head(test_events))


plot_sums(test_firefinder)


### Try with multiple files

# import a folder of sums data files
all_files <- file.path("input/sums/")
test_all_files <- import_folder(all_files)


all_sums <- apply_detector(test_all_files, threshold_detector, threshold=35, direction=">")
all_events <- list_events(all_sums)
summaries <- event_summaries(all_events)
kable(head(summaries))

```

