---
title: "Honduras R00 Intent-to-treat Models and Plots"
author: "Ethan Walker"
date: "14 March 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8, fig.height = 5)
```


```{r, include=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(pbkrtest)
library(emmeans)
library(broom)
library(purrr)
library(car)
library(forcats)
library(readxl)
library(naniar)
library(splines)
library(lubridate)
library(knitr)
library(influence.ME)
library(boxcoxmix)
jvPalette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
#load full dataset
# r00_full_joined_sphygmocor <- read_rds("output/r00_full_joined_sphygmocor.RDS")

# USE THIS DATASET FOR ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx
r00_model_data_outliers_removed <- read_rds("output/r00_model_data_outliers_removed.RDS")
```


```{r}
## Data prep
r00_model_data <- r00_model_data_outliers_removed %>% 
  mutate(sys_bp_central = as.numeric(sys_bp_central))%>% 
  mutate(dia_bp_central = as.numeric(dia_bp_central)) %>% 
  mutate(aug_index = as.numeric(aug_index)) %>% 
  mutate(aug_index_75 = as.numeric(aug_index_75)) %>% 
  mutate(pulse_pressure_periph = as.numeric(pulse_pressure_periph))%>% 
  mutate(pulse_pressure_central = as.numeric(pulse_pressure_central)) %>% 
  mutate(hr = as.numeric(hr)) %>% 
  mutate(bmi = as.numeric(bmi)) %>% 
  mutate(age_baseline = as.numeric(age_baseline)) %>% 
  mutate(phase = as.factor(phase)) %>%
  mutate(house_id = as.factor(house_id)) %>%
  #split age at 40; >40 = 1, <=40 = 0
  mutate(age_cat = if_else(age_baseline >= 40, ">=40", "<40")) %>% 
  mutate(age_cat = as.factor(age_cat)) %>% 
  #split bmi at 26; >26 = 1, <=26 = 0
  mutate(bmi_cat = if_else(bmi >= 26, ">=26", "<26")) %>% 
  mutate(bmi_cat = as.factor(bmi_cat)) %>%
  mutate(whr_cat = as.factor(whr_cat)) %>%
  mutate(season = as.factor(season)) %>%
  #pulse pressure amplification vars
  mutate(pulse_pressure_amp = as.numeric(pulse_pressure_periph - pulse_pressure_central)) %>%
  mutate(pulse_pressure_amp_ratio = as.numeric(pulse_pressure_periph/pulse_pressure_central)) %>%
  select(sys_bp_central, dia_bp_central, aug_index, aug_index_75, aug_pressure, 
         hr, pulse_pressure_periph, season, sys_bp_periph, dia_bp_periph, 
         pulse_pressure_central, assigned_stove, house_id, age_cat, age_current, 
         age_baseline, bmi_cat, bmi, phase, study_arm, date_sphygmo, whr_cat, 
         pulse_pressure_amp, pulse_pressure_amp_ratio, map_central, map_periph, med_bp) 

# Filtering out medication users
r00_model_data_meds <- r00_model_data %>% 
  #filtering out bp med users
  filter(is.na(med_bp))

r00_model_data_6phases <- r00_model_data %>% 
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) == 6)

r00_model_data_outliers_aix <- r00_model_data %>% 
  # removes 6 potential "outliers" with high or low AIx
  filter(aug_index < 75 | is.na(aug_index)) %>% 
  filter(aug_index > -25 | is.na(aug_index))

r00_model_data_outliers_cpp <- r00_model_data %>% 
  # removes 4 potential "outliers" > 75mmHg CPP
  filter(pulse_pressure_central < 75 | is.na(pulse_pressure_central))

r00_model_data_baseline <- r00_model_data %>% 
  filter(phase == 1)
r00_model_data_p2 <- r00_model_data %>% 
  filter(phase == 2)
r00_model_data_p3 <- r00_model_data %>% 
  filter(phase == 3)
r00_model_data_p4 <- r00_model_data %>% 
  filter(phase == 4)
r00_model_data_p5 <- r00_model_data %>% 
  filter(phase == 5)
r00_model_data_p6 <- r00_model_data %>% 
  filter(phase == 6)
```


```{r}
# USE THIS DATASET FOR ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx
## This dataset is already saved -- use code above to load
#r00_model_data_outliers_removed <- r00_full_joined_sphygmocor %>% 
  # removes 6 potential "outliers" with high or low AIx
  # removes 4 potential "outliers" > 75mmHg CPP
#  filter(aug_index < 75 | is.na(aug_index)) %>% 
#  filter(aug_index > -25 | is.na(aug_index)) %>% 
#  filter(pulse_pressure_central < 75 | is.na(pulse_pressure_central))
#write_rds(r00_model_data_outliers_removed, "output/r00_model_data_outliers_removed.rds")
```


# Simple linear models between AIx and age/bmi
```{r}
#AIx
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_baseline)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p2)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p3)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p4)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p5)
tidy(aix_age)
aix_age <- lm(aug_index ~ age_baseline, data = r00_model_data_p6)
tidy(aix_age)

aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_baseline)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p2)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p3)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p4)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p5)
tidy(aix_bmi)
aix_bmi <- lm(aug_index ~ bmi, data = r00_model_data_p6)
tidy(aix_bmi)
```

\pagebreak  

# AIx intent-to-treat analyses
```{r}
## Model Summaries
## Honduras R00 Initial AIx Models

##### AIx ITT base model - spline with 6 df
model_itt <- lmer(aug_index ~ assigned_stove + ns(date_sphygmo, df=6) + 
                 (1 | house_id), r00_model_data)
#summary(model_itt)
tidy_model_itt <- tidy(model_itt, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "primary", "na")) 


##### AIx ITT model - bp meds removed (57 obs)
model_no_bp_meds <- lmer(aug_index ~ assigned_stove + ns(date_sphygmo, df=6) + 
                 (1 | house_id), r00_model_data_meds)
#summary(model_no_bp_meds)
tidy_model_no_bp_meds <- tidy(model_no_bp_meds, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "no bp meds", "na")) 


##### AIx ITT model - phase instead of spline
model_phase <- lmer(aug_index ~ assigned_stove + phase + 
                 (1 | house_id), r00_model_data)
#summary(model_phase)
tidy_model_phase <- tidy(model_phase, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "phase", "na")) 


##### AIx ITT model - season instead of spline
model_season <- lmer(aug_index ~ assigned_stove + season + 
                 (1 | house_id), r00_model_data)
#summary(model_season)
tidy_model_season <- tidy(model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "season", "na")) 


##### AIx ITT model - participants who completed all 6 phases
model_6phases <- lmer(aug_index ~ assigned_stove + ns(date_sphygmo, df=6) +
                          (1 | house_id), r00_model_data_6phases)
# summary(model_6phases)
tidy_model_6phases <- tidy(model_6phases, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "6 phases", "na")) 


##### AIx ITT model - including baseline age
model_age <- lmer(aug_index ~ assigned_stove + ns(date_sphygmo, df=6) +
                  age_baseline + (1 | house_id), r00_model_data)
# summary(model_age)
tidy_model_age <- tidy(model_age, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "age", "na")) 


# Combine prepped data for plotting
aix_results <- rbind(tidy_model_itt,
                     tidy_model_no_bp_meds,
                     tidy_model_6phases,
                     tidy_model_phase,
                     tidy_model_season,
                     tidy_model_age)
```

\pagebreak  

# AIx Model Summaries and Plots
## Analyses with 6 outliers removed: 2 below -25 and 4 above 75
## Keep these outliers out for all future analyses (AIx and CPP)
```{r}
plot_estimates <- aix_results %>%
  mutate(model = factor(model, levels = c("primary", "no bp meds",
                                          "6 phases", "phase", "season", "age"))) %>% 
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "AIx ITT Models - Justa vs Traditional") +
  labs(y = "Estimate (%)") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 25, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```


\pagebreak  

# AIx ITT primary model diagnostic plots
```{r}
plot(model_itt, main = "AIx primary model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(model_itt), main = "AIx primary model QQ Plot")

#aix_influential <- influence(sphygmo_model_season, obs = TRUE)

#aix_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(aix_influential, which = "cook")
```

\pagebreak  


# Simple linear models between CPP and age/bmi
```{r}
#Central Pulse Pressure
cpp_age <- lm(pulse_pressure_central ~ age_baseline, data = r00_model_data_baseline)
tidy(cpp_age)

cpp_bmi <- lm(pulse_pressure_central ~ bmi, data = r00_model_data_baseline)
tidy(cpp_bmi)
```

\pagebreak  

# CPP intent-to-treat analyses
```{r}
## Model Summaries
## Honduras R00 Initial CPP Models

##### CPP ITT base model - spline with 6 df
model_itt <- lmer(pulse_pressure_central ~ assigned_stove + ns(date_sphygmo, df=6) + 
                 (1 | house_id), r00_model_data)
#summary(model_itt)
tidy_model_itt <- tidy(model_itt, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "primary", "na")) 


##### CPP ITT model - bp meds removed (57 obs)
model_no_bp_meds <- lmer(pulse_pressure_central ~ assigned_stove + ns(date_sphygmo, df=6) + 
                 (1 | house_id), r00_model_data_meds)
#summary(model_no_bp_meds)
tidy_model_no_bp_meds <- tidy(model_no_bp_meds, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "no bp meds", "na")) 


##### CPP ITT model - phase instead of spline
model_phase <- lmer(pulse_pressure_central ~ assigned_stove + phase + 
                 (1 | house_id), r00_model_data)
#summary(model_phase)
tidy_model_phase <- tidy(model_phase, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "phase", "na")) 


##### CPP ITT model - season instead of spline
model_season <- lmer(pulse_pressure_central ~ assigned_stove + season + 
                 (1 | house_id), r00_model_data)
#summary(model_season)
tidy_model_season <- tidy(model_season, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "season", "na")) 


##### CPP ITT model - participants who completed all 6 phases
model_6phases <- lmer(pulse_pressure_central ~ assigned_stove + ns(date_sphygmo, df=6) +
                          (1 | house_id), r00_model_data_6phases)
# summary(model_6phases)
tidy_model_6phases <- tidy(model_6phases, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "6 phases", "na")) 


##### CPP ITT model - including baseline age
model_age <- lmer(pulse_pressure_central ~ assigned_stove + ns(date_sphygmo, df=6) +
                  age_baseline + (1 | house_id), r00_model_data)
# summary(model_age)
tidy_model_age <- tidy(model_age, conf.int = TRUE) %>% 
    filter(grepl('assigned_stove1', term)) %>% 
    mutate(model = if_else(term == "assigned_stove1", "age", "na")) 


# Combine prepped data for plotting
cpp_results <- rbind(tidy_model_itt,
                     tidy_model_no_bp_meds,
                     tidy_model_6phases,
                     tidy_model_phase,
                     tidy_model_season,
                     tidy_model_age)
```

\pagebreak  

# CPP Model Summaries and Plots
```{r}
plot_estimates <- cpp_results %>%
  mutate(model = factor(model, levels = c("primary", "no bp meds",
                                          "6 phases", "phase", "season", "age"))) %>% 
  ggplot() +
  geom_point(aes(x=model, y=estimate), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "CPP ITT Models - Justa vs Traditional") +
  labs(y = "Estimate (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 19), 
          axis.text.x = element_text(angle = 25, hjust = 1, 
                                     size = 18, colour = "black"),
          axis.text.y = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_colour_manual(values=jvPalette) 
plot_estimates
```

\pagebreak  

# Central Pulse Pressure primary model diagnostic plots
```{r}
plot(model_itt, main = "Central Pulse Pressure primary model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(model_itt), main = "Central Pulse Pressure primary model QQ Plot")

#cpp_influential <- influence(sphygmo_model_season, obs = TRUE)

#cpp_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(cpp_influential, which = "cook")
```

