---
title: "SUMs Summary Statistics"
author: "Ethan Walker"
date: "16 Jan 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 6)
```

```{r, message=FALSE}
library(tidyverse)
library(knitr)
```

```{r, message=FALSE}
r00_full_repeated_by_phase <- read_rds("output/r00_full_repeated_by_phase.rds")
```

# Variables grouped by study arm
```{r}
summary_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Events 38C") %>% 
  #filter(phase == 1 | phase == 2) %>% 
  group_by(study_arm, phase) %>% 
  summarise_all(funs("_mean" = mean, "_sd" = sd, "_median" = median, 
                     "_min" = min, "_max" = max, "_n" = n())) %>% 
  gather(var, value, -study_arm, -phase) %>% 
  separate(var, into = c("var", "stat"), sep = "__") %>% 
  spread(stat, value) %>% 
  arrange(var, phase, study_arm) %>% 
  select(var, phase, study_arm, n, mean, sd, median, max, min) %>% 
  mutate(mean = round(mean, digits = 2), 
         sd = round(sd, digits = 2), 
         median = round(median, digits = 2), 
         max = round(max, digits = 2), 
         min = round(min, digits = 2)) %>% 
  rename("Variable" = var, "Phase" = phase, "Study Arm" = study_arm) 
kable(summary_primary_stoves, digits = 2)
```

\pagebreak  

# Boxplots by phase
## Percent time spent at specified temperature
## Primary Stoves
```{r}
# boxplots by phase, faceted by study arm
boxplots_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Percent 38C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 38C`)) +
  geom_boxplot(aes(phase, `Percent 38C`)) +
  ggtitle("Percent 38C by Phase and Study Arm", subtitle = "Primary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 38C") +
  theme_bw()
boxplots_primary_stoves
```

\pagebreak  

```{r}
boxplots_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Percent 40C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 40C`)) +
  geom_boxplot(aes(phase, `Percent 40C`)) +
  ggtitle("Percent 40C by Phase and Study Arm", subtitle = "Primary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 40C") +
  theme_bw()
boxplots_primary_stoves
```

\pagebreak  

```{r}
boxplots_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Percent 45C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 45C`)) +
  geom_boxplot(aes(phase, `Percent 45C`)) +
  ggtitle("Percent 45C by Phase and Study Arm", subtitle = "Primary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 45C") +
  theme_bw()
boxplots_primary_stoves
```

\pagebreak  

# Boxplots by phase
## Percent time spent at specified temperature
## Secondary Stoves
```{r}
# boxplots by phase, faceted by study arm
boxplots_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Percent 38C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 38C`)) +
  geom_boxplot(aes(phase, `Percent 38C`)) +
  ggtitle("Percent 38C by Phase and Study Arm", subtitle = "Secondary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 38C") +
  theme_bw()
boxplots_secondary_stoves
```

\pagebreak  

```{r}
boxplots_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Percent 40C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 40C`)) +
  geom_boxplot(aes(phase, `Percent 40C`)) +
  ggtitle("Percent 40C by Phase and Study Arm", subtitle = "Secondary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 40C") +
  theme_bw()
boxplots_secondary_stoves
```

\pagebreak  

```{r}
boxplots_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Percent 45C") %>% 
  mutate(study_arm = factor(study_arm, levels = c(1, 2), labels = c("Arm 1", "Arm 2"))) %>% 
  ggplot(aes(phase, `Percent 45C`)) +
  geom_boxplot(aes(phase, `Percent 45C`)) +
  ggtitle("Percent 45C by Phase and Study Arm", subtitle = "Secondary Stoves") +
  facet_wrap(~study_arm) +
  xlab("Study Phase") +
  ylab("Percent 45C") +
  theme_bw()
boxplots_secondary_stoves
```

\pagebreak  

# Histograms for frequency of measurements
## Number of events above specified temperature
## Event = > 1hr below specified temperature
## Primary Stoves
```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Events 38C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 38C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 38C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 38C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Events 40C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 40C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 40C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 40C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

```{r}
histogram_primary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_events, 
         "Events 40C" = sums_temp40_events, 
         "Events 45C" = sums_temp45_events, 
         "Percent 38C" = sums_temp38_percent, 
         "Percent 40C" = sums_temp40_percent, 
         "Percent 45C" = sums_temp45_percent) %>% 
  na.exclude("Events 45C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 45C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 45C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 45C by Phase", subtitle = "Primary Stoves") 
histogram_primary_stoves
```

\pagebreak  

# Histograms for frequency of measurements
## Number of events above specified temperature
## Event = > 1hr below specified temperature
## Secondary Stoves
```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Events 38C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 38C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 38C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 38C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```

\pagebreak  

```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Events 40C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 40C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 40C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 40C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```

\pagebreak  

```{r}
histogram_secondary_stoves <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, 
         "Events 38C" = sums_temp38_secondary_events, 
         "Events 40C" = sums_temp40_secondary_events, 
         "Events 45C" = sums_temp45_secondary_events, 
         "Percent 38C" = sums_temp38_secondary_percent, 
         "Percent 40C" = sums_temp40_secondary_percent, 
         "Percent 45C" = sums_temp45_secondary_percent) %>% 
  na.exclude("Events 45C") %>% 
    ggplot()+
    geom_histogram(aes(x = `Events 45C`), bins = 7) +
    facet_wrap(~phase, ncol = 2) +
    theme_bw() +
    scale_fill_manual(values=c("#33CC99",
                               "#339999",
                               "#FF9900",
                               "#330099")) +
   xlab("Events 45C") +
   ylab("Frequency") +
   theme(text = element_text(size = 16),
          legend.position= "none",
          plot.title = element_text(hjust = 0.5)) +
   ggtitle("Events 45C by Phase", subtitle = "Secondary Stoves") 
histogram_secondary_stoves
```
