---
title: "R00 Stove Use Models"
author: "Ethan Walker"
date: "17 July 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8, fig.height = 5)
```


```{r, include=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(pbkrtest)
library(emmeans)
library(broom)
library(purrr)
library(car)
library(forcats)
library(readxl)
library(naniar)
library(splines)
library(lubridate)
library(knitr)
library(influence.ME)
library(boxcoxmix)
library(gamm4)
library(sjstats)
library(rptR)
jvPalette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```


```{r}
# load full dataset
#r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds") 

#load dataset
r00_model_data_outliers_removed <- read_rds("output/r00_model_data_outliers_removed.RDS")

stove_use_data <- r00_model_data_outliers_removed %>% 
  # removes 6 observations for participant who wasn't assigned to a study arm
  filter(!is.na(study_arm)) %>% 
  # removes 22 observations for pregnancies
  filter(pregnant_new == 0) %>% 
  # further removes 196 observations (n=1162)
  filter(!is.na(aug_index)) 

# Dataset for participants who have AIx data for all 6 Phases (107 participants)
r00_data_6phases <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) == 6) %>% 
  ungroup()
  

# Dataset for participants who have AIx data for all <6 Phases
r00_data_5phases <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>% 
  ungroup() 


# Dataset removing 46 participants who missed AIx in phase 2 from sphygmo malfunction
r00_data_sphygmo_p2 <- r00_model_data_outliers_removed %>%
  # removes 6 observations for participant who wasn't assigned to a study arm
  filter(!is.na(study_arm)) %>% 
  mutate(sphygmo_missing_phase2 = as.numeric(sys_bp_final_nurse),
         sphygmo_missing_phase2 = if_else(sphygmo_missing_phase2 > 1, 1, 0),
         sphygmo_missing_phase2 = if_else(is.na(sphygmo_missing_phase2),
                                          0, sphygmo_missing_phase2)) %>%
  group_by(house_id) %>%
  filter(sum(sphygmo_missing_phase2) == 0) %>% 
  ungroup() %>% 
  filter(pregnant_new == 0) %>% 
  filter(!is.na(aug_index))  # 949 obs from 184 participants  


# Filtering out medication users (n=34 obs)
r00_model_data_meds <- stove_use_data %>% 
  #filtering out bp med users
  filter(is.na(med_bp)) 
```


# Other "test" datasets when assessing missing data and selection bias
## Saving in case I need it for future analyses
## DO NOT USE THIS CHUNK OF CODE ##
```{r}
# load full dataset
#r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")

# USE THIS DATASET FOR ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx (10 total)
r00_model_data_outliers_removed <- read_rds("output/r00_model_data_outliers_removed.RDS") 

stove_use_data <- r00_model_data_outliers_removed %>% 
  # removed MOM054 who moved and wasn't assigned to a study arm
  filter(!is.na(assigned_stove)) %>% 
  # filter out 22 instances of pregnancy
  filter(pregnant_new == 0) %>% 
  filter(!is.na(aug_index)) %>% 
  mutate(age_multicat = cut(age_baseline, seq(20, 60, 10)),
         age_multicat = factor(age_multicat,
                               levels = c("(20,30]", "(30,40]", "(40,50]", "(50,60]"),
                               labels = c("20-30", "30-40", "40-50", "50-60")))


test_data <- r00_56_combined %>% 
  mutate(test = if_else(all_phases == "no" & stove_use_3 == "trad" & phase == 2 
                        & study_arm == 2, 1, 0)) %>% 
  group_by(house_id) %>% 
  filter(sum(test) == 0) %>% 
  ungroup() 



# Dataset for participants who have AIx data for all 6 Phases (107 participants)
r00_data_6phases <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) == 6) %>% 
  mutate(all_phases = "yes") %>% 
  ungroup() 

# Dataset for participants who have AIx data for all <6 Phases
r00_data_5phases <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>% 
  mutate(all_phases = "no") %>% 
  ungroup() 

# combine 6 phases and <6 phases datasets with indicator variable to group by
r00_56_combined <- rbind(r00_data_6phases, r00_data_5phases)

# Creating datasets for sensitivity analysis
## based on odd high/low values seen in participants who missed at least one phase
## seen when assessing mean AIx grouped by stove_use_3 and phase
r00_data_phase2 <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>%
  mutate(phase_2 = if_else(stove_use_3 == "trad" & phase==2,
                            1, 0),
         phase_2 = if_else(phase==3, lag(phase_2), phase_2),
         phase_2 = if_else(phase==4, lag(phase_2), phase_2),
         phase_2 = if_else(phase==5, lag(phase_2), phase_2),
         phase_2 = if_else(phase==6, lag(phase_2), phase_2),
         phase_2 = if_else(phase==1, lead(phase_2), phase_2)) %>% 
  select(house_id, phase, phase_2) %>% 
  filter(phase_2 == 1) %>%    # filtered down to 244 obs from 56 participants
  #summarise(n())
  ungroup()

r00_data_phase3low <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>%
  mutate(phase_3low = if_else(stove_use_3 == "trad" 
                            & phase==3, 1, 0),
         phase_3low = if_else(phase==4, lag(phase_3low), phase_3low),
         phase_3low = if_else(phase==5, lag(phase_3low), phase_3low),
         phase_3low = if_else(phase==6, lag(phase_3low), phase_3low),
         phase_3low = if_else(phase==2, lead(phase_3low), phase_3low),
         phase_3low = if_else(phase==1, lead(phase_3low), phase_3low)) %>% 
  select(house_id, phase, phase_3low) %>% 
  filter(phase_3low == 1) %>%     # filtered down to 226 obs from 49 participants
  ungroup()

r00_data_phase3hi <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>%
  mutate(phase_3hi = if_else(stove_use_3 == "justa/imprvd" 
                            & phase==3, 1, 0),
         phase_3hi = if_else(phase==4, lag(phase_3hi), phase_3hi),
         phase_3hi = if_else(phase==5, lag(phase_3hi), phase_3hi),
         phase_3hi = if_else(phase==6, lag(phase_3hi), phase_3hi),
         phase_3hi = if_else(phase==2, lead(phase_3hi), phase_3hi),
         phase_3hi = if_else(phase==1, lead(phase_3hi), phase_3hi)) %>% 
  select(house_id, phase, phase_3hi) %>% 
  filter(phase_3hi == 1) %>%     # filtered down to 81 obs from 17 participants
  ungroup()
  
r00_data_phase4 <- stove_use_data %>%
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) < 6) %>%
  mutate(phase_4 = if_else(stove_use_3 == "justa/imprvd" 
                            & phase==4, 1, 0),
         phase_4 = if_else(phase==5, lag(phase_4), phase_4),
         phase_4 = if_else(phase==6, lag(phase_4), phase_4),
         phase_4 = if_else(phase==3, lead(phase_4), phase_4),
         phase_4 = if_else(phase==2, lead(phase_4), phase_4),
         phase_4 = if_else(phase==1, lead(phase_4), phase_4)) %>% 
  select(house_id, phase, phase_4) %>% 
  filter(phase_4 == 1) %>%      # filtered down to 77 obs from 16 participants
  ungroup()

r00_phase34_filter_data <- r00_data_phase3low %>% 
  full_join(r00_data_phase3hi, by = c("house_id", "phase")) %>% 
  full_join(r00_data_phase4, by = c("house_id", "phase")) %>% 
  mutate(filter_phase34 = as.numeric(1)) %>% 
  full_join(stove_use_data, by = c("house_id", "phase")) %>% 
  mutate(filter_phase34 = if_else(is.na(filter_phase34), 0, 1)) %>% 
  filter(filter_phase34 == 0)
  
r00_highlow_data <- r00_data_phase2 %>% 
  full_join(r00_data_phase3low, by = c("house_id", "phase")) %>% 
  full_join(r00_data_phase3hi, by = c("house_id", "phase")) %>% 
  full_join(r00_data_phase4, by = c("house_id", "phase")) %>%
  mutate(filter_highlow = as.numeric(1))      # 440 obs from 97 participants

highlow_filter_data <- stove_use_data %>% 
  full_join(r00_highlow_data, by = c("house_id", "phase")) %>% 
  mutate(filter_highlow = if_else(is.na(filter_highlow), 0, 1)) %>% 
  filter(filter_highlow == 0)   # filtered to 722 obs from 133 participants

low_filter_data <- stove_use_data %>% 
  full_join(r00_highlow_data, by = c("house_id", "phase")) %>% 
  mutate(filter_low = if_else(phase_2==1 | phase_3low==1, 1, 0),
         filter_low = if_else(is.na(filter_low), 0, filter_low)) %>% 
  #select(house_id, phase, phase_2, phase_3low, filter_low)
  filter(filter_low == 0)   # filtered to  795 obs from 148 participants

hi_filter_data <- stove_use_data %>% 
  full_join(r00_highlow_data, by = c("house_id", "phase")) %>% 
  mutate(filter_hi = if_else(phase_4==1 | phase_3hi==1, 1, 0),
         filter_hi = if_else(is.na(filter_hi), 0, filter_hi)) %>% 
  #select(house_id, phase, phase_2, phase_3low, filter_low)
  filter(filter_hi == 0)    # filtered to  1047 obs from 206 participants


# Dataset filtering out 46 participants with no sphygmocor data from phase 2
sphygmo_p2_data <- r00_model_data_outliers_removed %>% 
  # removed MOM054 who moved and wasn't assigned to a study arm
  filter(!is.na(assigned_stove)) %>% 
  mutate(sys_bp_final_nurse = as.numeric(sys_bp_final_nurse)) %>% 
  mutate(phase2_sphygmo = 1) %>% 
  mutate(phase2_sphygmo = if_else(!is.na(sys_bp_final_nurse), 0, phase2_sphygmo),
         phase2_sphygmo = if_else(phase == 2 & pregnant_new == 1, 0, phase2_sphygmo)) %>% 
  group_by(house_id) %>% 
  filter(sum(phase2_sphygmo) == 6) %>% 
  ungroup() %>% 
  filter(pregnant_new == 0)

# Dataset filtering out 16 participants who were pregnant during any phase
no_pregnant_data <- r00_model_data_outliers_removed %>%
  mutate(p1_preg = if_else(phase == 1 & ((date_sphygmo - child_born_date) < 365), 1, 0)) %>% 
  mutate(p1_preg = as.numeric(p1_preg)) %>%
  mutate(pregnant_ever = 0) %>% 
  mutate(pregnant_ever = if_else(pregnant_new == 1 | p1_preg == 1, 1, pregnant_ever)) %>% 
  group_by(house_id) %>% 
  filter(sum(pregnant_ever) == 0) %>% 
  ungroup()

# Missed sessions due to pregnancy, refusal, etc
house_id <- c("ANT011", "ANT020", "ANT039", "ANT042", "CAC034", "CAC042",
                     "CAC060", "CAC062", "CAC063", "CER010", "CER021", "CER023",
                     "CER036", "CER042", "CER065", "CER068", "HOR041", "HOR071",
                     "MOM001", "MOM026", "MOM031", "MOM043", "MOM051", "MOM054",
                     "MOM061", "MOM062", "OLO053", "OLO078", "OLO102", "PER002",
                     "PER015", "PER018", "PER028", "PER035", "PER037", "PER046",
                     "PER057", "PER058", "PER059", "PER067", "PER068", "QDL017",
                     "QDL018", "QDL019", "QDL024", "QDL025", "QDL026", "QDL027",
                     "ZAC003", "ZAC004", "ZAC006", "ZAC014", "ZAC016", "ZAC022",
                     "ZAC027", "ZAC090", "ZAC095", "ZAC097", "OLO093", "ZAC098")
missed_sessions <- as.data.frame(house_id) %>% 
  mutate(missed = 1)

# database filtering out participants who missed a session (n=171)
missed_sessions_data <- r00_model_data_outliers_removed %>% 
  # removed MOM054 who moved and wasn't assigned to a study arm
  filter(!is.na(assigned_stove)) %>% 
  full_join(missed_sessions, by = "house_id") %>% 
  mutate(missed = as.numeric(missed)) %>% 
  filter(is.na(missed)) 
  
# Dataset for participants who did not miss phase 2
r00_model_data_phase2 <- stove_use_data %>% 
  mutate(phase2 = 1) %>% 
  mutate(phase2 = if_else(phase == 2 & is.na(aug_index), 0, phase2)) %>%  
  group_by(house_id) %>% 
  filter(sum(phase2) == 6) %>% 
  ungroup() 
```

# Analysis plan
## New variables here are already incorporated into the full database
```{r}
# stratify assigned stove and stove-use variables
table(stove_use_data$assigned_stove, stove_use_data$stove_use_3)

test_data <- r00_model_data_outliers_removed %>% 
  filter(!is.na(assigned_stove)) %>% 
  # mutating so NAs are reported as 0
  # days_sec is self-reported use of secondary stove in days/month
  mutate(days_sec = as.numeric(days_sec),
         days_sec = if_else(days_sec == 0 | is.na(days_sec), 0, days_sec)) %>% 
  # days_sec is self-reported use of secondary stove in days/month
  mutate(hours_primary = as.numeric(hours_primary),
         hours_primary = if_else(hours_primary == 0 | is.na(hours_primary), 
                                 0, hours_primary))

median(test_data$days_sec) # 1 day
hist(test_data$days_sec, breaks = 30)
median(test_data$hours_primary) # 3 hours
hist(test_data$hours_primary)
# Could dichotomize days_sec at 0 days or 1+ days
table(test_data$days_sec)
# However, the group of interest (justa+trad) only reported 0 days/month 14 times
# Consider dichotomizing days_sec at < 4 or 4+ days per month
table(test_data$days_sec, test_data$stove_use_3)
# Could dichotomize hours_primary at median of 3 (<3.5, 3.5+)
table(test_data$hours_primary)
table(test_data$hours_primary, test_data$stove_use_3)

# dataset with new variables for analysis
stove_use_data <- test_data %>% 
  # splitting days_sec at <4 and 4+
  mutate(days_sec_4 = if_else(days_sec < 4, 0, 1)) %>%
  mutate(days_sec_4 = factor(days_sec_4, levels = c(0,1), labels = c("<4", "4+"))) %>%
  # splitting hours_primary at <3.5 and 3.5+
  mutate(hours_primary_3.5 = if_else(hours_primary < 3.5, 0, 1)) %>%
  mutate(hours_primary_3.5 = factor(hours_primary_3.5, 
                                    levels = c(0,1), labels = c("<3.5", "3.5+"))) %>%
  # mutating stove_use_3 to character for use in if_else statement
  mutate(stove_use_3 = as.character(stove_use_3)) %>% 
  # new variable incorporating days/month of secondary stove use (<4 vs 4+) 
  # only doing this for justa+trad levels
  ## because only 24 people reported 4+ days improved secondary stove use with Justa
  ## and this data wasn't available in phase 1
  mutate(stove_use_days_stack = 
         if_else(stove_use_3 == "justa+trad" & days_sec_4 == "4+",
                 "justa+trad, 4+", stove_use_3)) %>% 
  mutate(stove_use_days_stack = 
           factor(stove_use_days_stack,
                  levels = c("justa/imprvd", "justa+trad", 
                             "justa+trad, 4+", "trad"),
                  labels = c("justa/imprvd", "justa+trad, <4", 
                             "justa+trad, 4+", "trad"))) %>%
  # reorder new var so traditional is reference
  mutate(stove_use_days_stack = 
           factor(stove_use_days_stack,
                  levels = c("trad", "justa+trad, 4+", 
                             "justa+trad, <4", "justa/imprvd"))) %>%
  # new variable incorporating hours/day of primary stove use (<3.5 vs 3.5+) 
  mutate(stove_use_hours = 
         if_else(stove_use_3 == "justa+trad" & hours_primary_3.5 == "3.5+",
                 "justa+trad, 3.5+", stove_use_3)) %>% 
  mutate(stove_use_hours = 
         if_else(stove_use_hours == "trad" & hours_primary_3.5 == "3.5+",
                 "trad, 3.5+", stove_use_hours)) %>% 
  mutate(stove_use_hours = 
         if_else(stove_use_hours == "justa/imprvd" & hours_primary_3.5 == "3.5+",
                 "justa/imprvd, 3.5+", stove_use_hours)) %>% 
  mutate(stove_use_hours = 
           factor(stove_use_hours,
                  levels = c("justa/imprvd", "justa/imprvd, 3.5+", "justa+trad", 
                             "justa+trad, 3.5+", "trad", "trad, 3.5+"),
                  labels = c("justa/imprvd, <3.5", "justa/imprvd, 3.5+", "justa+trad, <3.5", 
                             "justa+trad, 3.5+", "trad, <3.5", "trad, 3.5+"))) %>%
  # reorder new var so traditional 3.5+ hours is reference
  mutate(stove_use_hours = 
           factor(stove_use_hours,
                  levels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+", 
                             "justa+trad, <3.5", "justa/imprvd, 3.5+", 
                             "justa/imprvd, <3.5"))) %>%
  mutate(stove_use_3 = factor(stove_use_3, 
                            levels = c("trad", "justa+trad", "justa/imprvd")))

table(stove_use_data$days_sec_4, stove_use_data$stove_use_3)
table(stove_use_data$days_sec_4, stove_use_data$stove_use_days_stack)
table(stove_use_data$hours_primary_3.5, stove_use_data$stove_use_3)
table(stove_use_data$hours_primary_3.5, stove_use_data$stove_use_hours)
```

# Describe actual stove use over course of study, by assigned study arm
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds") %>% 
  # removes 6 observations for participant who wasn't assigned to a study arm
  filter(!is.na(study_arm)) %>% 
  # removes 22 observations for pregnancies
  filter(pregnant_new == 0)

stove_use <- r00_full_long %>% 
  select(house_id, study_arm, phase, stove_use_3) %>% 
  spread(phase, stove_use_3) %>%  # new columns for phase, filled in by stove use
  unite(stove, c("1":"6"), sep = ", ") %>%  # unite new columns into one new column
  arrange(study_arm)

# create new dataframe from a frequency table of stove use options by study arm
stove_use_options <- as.data.frame(table(stove_use$stove, stove_use$study_arm)) %>% 
  rename(stove_use_combination = Var1) %>% 
  rename(study_arm = Var2) %>% 
  rename(freq = Freq) %>% 
  arrange(study_arm, desc(freq)) %>% 
  filter(freq != 0)

#write_csv(stove_use_options, "output/stove_use_options.csv")

##### assign stove-use var to participants based on above table

stove_use_2 <- r00_full_long %>% 
  #select(house_id, study_arm, phase, stove_use_3) %>% 
  mutate(dummy_var = factor(stove_use_3, 
                            levels = c("trad", "justa+trad", "justa/imprvd"),
                            labels = c(1, 2, 3))) %>% 
  mutate(dummy_var = as.numeric(dummy_var),
         dummy_var = if_else(is.na(dummy_var), 0, dummy_var),
         dummy_var = if_else(dummy_var == 1, 1, dummy_var),
         dummy_var = if_else(dummy_var == 2, 10, dummy_var),
         dummy_var = if_else(dummy_var == 3, 100, dummy_var)) %>% 
  group_by(house_id) %>% 
  # code below designates participants into 3 groups: compliers, stackers, and inconsistent
  # compliers used the assigned stove based on their study arm assignment
  # stackers used the assigned stove based on study arm, but stacked with traditional
  # inconsistent meant they switched groups, didn't follow stove assignment, or missed 2+ visits
  # stackers/compliers were allowed to miss 1 pre-intervention visit 
    # or 1 post-intervention visit and still meet the above definitions
  mutate(stove_use_label = if_else(study_arm == 1 & 
                                         (sum(dummy_var) == 42 | sum(dummy_var) == 32 |
                                          sum(dummy_var) == 41),
                                         "stacker", "inconsistent"),
         stove_use_label = if_else(study_arm == 1 & 
                                         (sum(dummy_var) == 402 | sum(dummy_var) == 302 |
                                          sum(dummy_var) == 401),
                                         "complier", stove_use_label),
         stove_use_label = if_else(study_arm == 2 & 
                                         (sum(dummy_var) == 24 | sum(dummy_var) == 14 |
                                          sum(dummy_var) == 23),
                                         "stacker", stove_use_label),
         stove_use_label = if_else(study_arm == 2 & 
                                         (sum(dummy_var) == 204 | sum(dummy_var) == 104 |
                                          sum(dummy_var) == 203),
                                         "complier", stove_use_label)) %>% 
  ungroup() 
  #filter(phase == 1) %>% 
  #group_by(stove_use_label, phase) %>% 
  #summarise(mean(aug_index, na.rm = TRUE), n())

table(stove_use_2$stove_use_label, stove_use_2$study_arm)

stove_use_3 <- stove_use_2 %>% 
  select(house_id, study_arm, phase, stove_use_3, stove_use_label) %>% 
  spread(phase, stove_use_3) %>%  # new columns for phase, filled in by stove use
  unite(stove, c("1":"6"), sep = ", ") %>%  # unite new columns into one new column
  arrange(study_arm)

# merge datasets to capture new stove-use designations
stove_use_options_2 <- stove_use_3 %>% 
  rename(stove_use_combination = stove) %>% 
  right_join(stove_use_options, by = c("stove_use_combination", "study_arm")) %>% 
  select(-house_id) %>% 
  unique()

#write_csv(stove_use_options_2, "output/stove_use_options_2.csv")
```

# Stove use analyses with a priori confounders
```{r}
# AIx and Stove use variables
## tried: prim_sum_temp_percent_50 (and other SUMs vars), prim_stove_loc, hours_primary,
## hours_primary_3.5, community (random and fixed), days_sec, times_cook,
## dds_total, ses_materials, beds_new, salt_cat, sugar_cat, manteca_cat, elevation,
## haptrash_freq, hapsmoke_freq, mean_hum, mean_dew, mean_temp, max_temp, max_hum, max_dew,
## sec_stove, sums, hours_secondary, SES_weighted_sum, ses_weighted_cat, enclosure, 
## condition


##### Complete-case model 
model_6phases <- lmer(aug_index ~ stove_use_3 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_6phases)
tidy_model_6phases <- tidy(model_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "complete case")
#icc(model_6phases)

################################################################
##### Missed phases model 
model_5phases <- lmer(aug_index ~ stove_use_3 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_5phases)
tidy_model_5phases <- tidy(model_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "missed visit")
#icc(model_5phases)

################################################################
model_stove_use_3 <- lmer(aug_index ~ stove_use_3 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_stove_use_3)
#icc(model_stove_use_3)
tidy_model_stove_use_3 <- tidy(model_stove_use_3, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "all data") 

################################################################
model_p2_sphygmo <- lmer(aug_index ~ stove_use_3 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_p2_sphygmo)
#icc(model_p2_sphygmo)
tidy_model_p2_sphygmo <- tidy(model_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
model_compliance <- lmer(aug_index ~ stove_use_label + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_2)
#summary(model_compliance)
#icc(model_compliance)
tidy_model_compliance <- tidy(model_compliance, conf.int = TRUE) %>% 
    filter(grepl('stove_use_label', term)) %>% 
    mutate(model = "compliance") 

################################################################
##### bp meds removed
model_no_bp_meds <- lmer(aug_index ~ stove_use_3 + 
                             ns(date_sphygmo, df=6) + age_baseline +
                             waist_cm + school_bi + (1 | house_id), 
                             r00_model_data_meds)
#summary(model_no_bp_meds)
tidy_model_no_bp_meds <- tidy(model_no_bp_meds, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "no bp meds")

################################################################
##### date spline with 12 df
model_spline12 <- lmer(aug_index ~ stove_use_3 + 
                           ns(date_sphygmo, df=12) + age_baseline +
                           waist_cm + school_bi + (1 | house_id), 
                           stove_use_data)
#summary(model_spline12)
tidy_model_spline12 <- tidy(model_spline12, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "spline 12 df")

################################################################
##### phase instead of spline
model_phase <- lmer(aug_index ~ stove_use_3 + phase + age_baseline +
                        waist_cm + school_bi + (1 | house_id), 
                    stove_use_data)
#summary(model_phase)
tidy_model_phase <- tidy(model_phase, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "visit")

################################################################
##### season instead of spline
model_season <- lmer(aug_index ~ stove_use_3 + season + age_baseline +
                         waist_cm + school_bi + (1 | house_id), 
                     stove_use_data)
#summary(model_season)
tidy_model_season <- tidy(model_season, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "season")

################################################################
##### bmi instead of waist_cm
model_bmi <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                      bmi + school_bi + (1 | house_id), 
                  stove_use_data)
#summary(model_bmi)
tidy_model_bmi <- tidy(model_bmi, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "bmi")

################################################################
##### whr instead of waist_cm
model_whr <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                      whr + school_bi + (1 | house_id), 
                  stove_use_data)
#summary(model_whr)
tidy_model_whr <- tidy(model_whr, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "whr")

################################################################
##### adding beds_new
model_beds <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                       waist_cm + school_bi + beds_new + (1 | house_id), 
                   stove_use_data)
#summary(model_beds)
tidy_model_beds <- tidy(model_beds, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "beds")

################################################################
##### adding ses_materials
model_ses <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                      waist_cm + school_bi + ses_materials + (1 | house_id), 
                  stove_use_data)
#summary(model_ses)
tidy_model_ses <- tidy(model_ses, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "ses assets")

################################################################
##### adding phys_act
model_pa <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                     waist_cm + school_bi + phys_act + (1 | house_id), 
                 stove_use_data)
#summary(model_pa)
tidy_model_pa <- tidy(model_pa, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "phys act")

################################################################
##### adding dds_total
model_dds <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                      waist_cm + school_bi + dds_total + (1 | house_id), 
                  stove_use_data)
#summary(model_dds)
tidy_model_dds <- tidy(model_dds, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "dds")

################################################################
##### full model with all potential confounders
model_full <- lmer(aug_index ~ stove_use_3 + ns(date_sphygmo, df=6) + age_baseline +
                       waist_cm + school_bi + dds_total + phys_act +
                       ses_materials + beds_new + 
                       (1 | house_id), stove_use_data)
#summary(model_full)
tidy_model_full <- tidy(model_full, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "full")

################################################################
######################################### stove_use_4
##### Complete-case model 
model_4level_6phases <- lmer(aug_index ~ stove_use_4 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_4level_6phases)
tidy_model_4level_6phases <- tidy(model_4level_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "complete case")
#icc(model_4level_6phases)

################################################################
##### Missed phases model 
model_4level_5phases <- lmer(aug_index ~ stove_use_4 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_4level_5phases)
tidy_model_4level_5phases <- tidy(model_4level_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "missed visit")
#icc(model_4level_5phases)

################################################################
model_4level <- lmer(aug_index ~ stove_use_4 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_4level)
#icc(model_4level)
tidy_model_4level <- tidy(model_4level, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "all data") 

################################################################
model_4level_p2_sphygmo <- lmer(aug_index ~ stove_use_4 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_4level_p2_sphygmo)
#icc(model_4level_p2_sphygmo)
tidy_model_4level_p2_sphygmo <- tidy(model_4level_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
######################################### stove_use_days_stack
##### Complete-case model 
model_days_6phases <- lmer(aug_index ~ stove_use_days_stack + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_days_6phases)
tidy_model_days_6phases <- tidy(model_days_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "complete case")
#icc(model_days_6phases)

################################################################
##### Missed phases model 
model_days_5phases <- lmer(aug_index ~ stove_use_days_stack + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_days_5phases)
tidy_model_days_5phases <- tidy(model_days_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "missed visit")
#icc(model_days_5phases)

################################################################
model_days <- lmer(aug_index ~ stove_use_days_stack + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_days)
#icc(model_days)
tidy_model_days <- tidy(model_days, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "all data") 

################################################################
model_days_p2_sphygmo <- lmer(aug_index ~ stove_use_days_stack + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_days_p2_sphygmo)
#icc(model_days_p2_sphygmo)
tidy_model_days_p2_sphygmo <- tidy(model_days_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
######################################### stove_use_hours
##### Complete-case model 
model_hours_6phases <- lmer(aug_index ~ stove_use_hours + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_hours_6phases)
tidy_model_hours_6phases <- tidy(model_hours_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "complete case")
#icc(model_hours_6phases)

################################################################
##### Missed phases model 
model_hours_5phases <- lmer(aug_index ~ stove_use_hours + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_hours_5phases)
tidy_model_hours_5phases <- tidy(model_hours_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "missed visit")
#icc(model_hours_5phases)

################################################################
model_hours <- lmer(aug_index ~ stove_use_hours + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_hours)
#icc(model_hours)
tidy_model_hours <- tidy(model_hours, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "all data") 

################################################################
model_hours_p2_sphygmo <- lmer(aug_index ~ stove_use_hours + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_hours_p2_sphygmo)
#icc(model_hours_p2_sphygmo)
tidy_model_hours_p2_sphygmo <- tidy(model_hours_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
aix_results_3level <- rbind(tidy_model_6phases,
                     tidy_model_5phases,
                     tidy_model_stove_use_3,
                     tidy_model_p2_sphygmo,
                     tidy_model_no_bp_meds,
                     tidy_model_phase,
                     tidy_model_season,
                     tidy_model_spline12,
                     tidy_model_bmi,
                     tidy_model_whr,
                     tidy_model_beds,
                     tidy_model_ses,
                     tidy_model_pa,
                     tidy_model_dds)

aix_results_4level <- rbind(tidy_model_4level_6phases,
                     tidy_model_4level_5phases,
                     tidy_model_4level,
                     tidy_model_4level_p2_sphygmo)

aix_results_days <- rbind(tidy_model_days_6phases,
                     tidy_model_days_5phases,
                     tidy_model_days,
                     tidy_model_days_p2_sphygmo)

aix_results_hours <- rbind(tidy_model_hours_6phases,
                     tidy_model_hours_5phases,
                     tidy_model_hours,
                     tidy_model_hours_p2_sphygmo)

#kable(aix_results)
```

## Plot model estimates - AIx and Stove Use
```{r}
# primary stove-use model with sensitivity analyses
plot_estimates <- aix_results_3level %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2", 
                                          "no bp meds", "visit", "season", "spline 12 df", 
                                          "bmi", "whr", "beds", "ses assets", "dds",
                                          "phys act"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_3justa+trad", "stove_use_3justa/imprvd"),
                        labels = c("justa+trad", "justa/imprvd"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with \n or without secondary stove (%)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8), 
                     labels = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8)) 

plot_estimates


# stove use 4-level
plot_estimates <- aix_results_4level %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_4justa+trad",
                                   "stove_use_4justa+imp",
                                   "stove_use_4justa"),
                        labels = c("justa+trad", "justa+imp", "justa"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with \n or without secondary stove (%)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9), 
                     labels = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9)) 
plot_estimates


# stove use days/month model
plot_estimates <- aix_results_days %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_days_stackjusta+trad, 4+",
                                   "stove_use_days_stackjusta+trad, <4",
                                   "stove_use_days_stackjusta/imprvd"),
                        labels = c("justa+trad 4+ days/month", "justa+trad <4 days/month",
                                   "justa/imprvd"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with \n or without secondary stove (%)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9), 
                     labels = c(-4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9)) 
plot_estimates


# stove use hours/day model
plot_estimates <- aix_results_hours %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_hourstrad, <3.5",
                                   "stove_use_hoursjusta+trad, 3.5+",
                                   "stove_use_hoursjusta+trad, <3.5",
                                   "stove_use_hoursjusta/imprvd, 3.5+",
                                   "stove_use_hoursjusta/imprvd, <3.5"),
                        labels = c("trad <3.5 hours", "justa+trad 3.5+ hours",
                                   "justa+trad <3.5 hours", "justa/imprvd 3.5+ hours",
                                   "justa/imprvd <3.5 hours"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.75), size = 4) +
  scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.75), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove \n use 3.5+ hours/day (%)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), 
                     labels = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10)) 
plot_estimates


# stove use - compliance
plot_estimates <- tidy_model_compliance %>%
  mutate(level = factor(term, 
                        levels = c("stove_use_labelinconsistent",
                                   "stove_use_labelstacker"),
                        labels = c("inconsistent", "stacker"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.75), size = 4) +
  scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.75), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs compliant \n stove users (%)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), 
                     labels = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10)) 
plot_estimates
```

# AIx primary model diagnostic plots - stove use
```{r}
plot(model_stove_use_3, main = "AIx and stove-use model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(model_stove_use_3), main = "AIx and stove-use model")


#aix_influential <- influence(model_stove_use_3, obs = TRUE)

#aix_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(aix_influential, which = "cook")
```



# Stove use analyses with a priori confounders
```{r}
# CPP and Stove use variables

##### Complete-case model 
model_6phases <- lmer(pulse_pressure_central ~ stove_use_3 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_6phases)
tidy_model_6phases <- tidy(model_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "complete case")
#icc(model_6phases)

################################################################
##### Missed phases model 
model_5phases <- lmer(pulse_pressure_central ~ stove_use_3 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_5phases)
tidy_model_5phases <- tidy(model_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "missed visit")
#icc(model_5phases)

################################################################
model_stove_use_3 <- lmer(pulse_pressure_central ~ stove_use_3 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_stove_use_3)
#icc(model_stove_use_3)
tidy_model_stove_use_3 <- tidy(model_stove_use_3, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "all data") 

################################################################
model_p2_sphygmo <- lmer(pulse_pressure_central ~ stove_use_3 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_p2_sphygmo)
#icc(model_p2_sphygmo)
tidy_model_p2_sphygmo <- tidy(model_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
model_compliance <- lmer(pulse_pressure_central ~ stove_use_label + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_2)
#summary(model_compliance)
#icc(model_compliance)
tidy_model_compliance <- tidy(model_compliance, conf.int = TRUE) %>% 
    filter(grepl('stove_use_label', term)) %>% 
    mutate(model = "compliance") 

################################################################
##### bp meds removed
model_no_bp_meds <- lmer(pulse_pressure_central ~ stove_use_3 + 
                             ns(date_sphygmo, df=6) + age_baseline +
                             waist_cm + school_bi + (1 | house_id), 
                             r00_model_data_meds)
#summary(model_no_bp_meds)
tidy_model_no_bp_meds <- tidy(model_no_bp_meds, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "no bp meds")

################################################################
##### date spline with 12 df
model_spline12 <- lmer(pulse_pressure_central ~ stove_use_3 + 
                           ns(date_sphygmo, df=12) + age_baseline +
                           waist_cm + school_bi + (1 | house_id), 
                           stove_use_data)
#summary(model_spline12)
tidy_model_spline12 <- tidy(model_spline12, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "spline 12 df")

################################################################
##### phase instead of spline
model_phase <- lmer(pulse_pressure_central ~ stove_use_3 + 
                      phase + age_baseline +
                        waist_cm + school_bi + (1 | house_id), 
                    stove_use_data)
#summary(model_phase)
tidy_model_phase <- tidy(model_phase, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "visit")

################################################################
##### season instead of spline
model_season <- lmer(pulse_pressure_central ~ stove_use_3 + 
                       season + age_baseline +
                         waist_cm + school_bi + (1 | house_id), 
                     stove_use_data)
#summary(model_season)
tidy_model_season <- tidy(model_season, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "season")

################################################################
##### bmi instead of waist_cm
model_bmi <- lmer(pulse_pressure_central ~ stove_use_3 + 
                    ns(date_sphygmo, df=6) + age_baseline +
                      bmi + school_bi + (1 | house_id), 
                  stove_use_data)
#summary(model_bmi)
tidy_model_bmi <- tidy(model_bmi, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "bmi")

################################################################
##### whr instead of waist_cm
model_whr <- lmer(pulse_pressure_central ~ stove_use_3 + 
                    ns(date_sphygmo, df=6) + age_baseline +
                      whr + school_bi + (1 | house_id), 
                  stove_use_data)
#summary(model_whr)
tidy_model_whr <- tidy(model_whr, conf.int = TRUE) %>% 
    filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "whr")

################################################################
##### adding beds_new
model_beds <- lmer(pulse_pressure_central ~ stove_use_3 + 
                     ns(date_sphygmo, df=6) + age_baseline +
                       waist_cm + school_bi + beds_new + (1 | house_id), 
                   stove_use_data)
#summary(model_beds)
tidy_model_beds <- tidy(model_beds, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "beds")

################################################################
##### adding ses_materials
model_ses <- lmer(pulse_pressure_central ~ stove_use_3 + 
                    ns(date_sphygmo, df=6) + age_baseline +
                      waist_cm + school_bi + ses_materials + (1 | house_id), 
                  stove_use_data)
#summary(model_ses)
tidy_model_ses <- tidy(model_ses, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "ses assets")

################################################################
##### adding phys_act
model_pa <- lmer(pulse_pressure_central ~ stove_use_3 + 
                   ns(date_sphygmo, df=6) + age_baseline +
                     waist_cm + school_bi + phys_act + (1 | house_id), 
                 stove_use_data)
#summary(model_pa)
tidy_model_pa <- tidy(model_pa, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "phys act")

################################################################
##### adding dds_total
model_dds <- lmer(pulse_pressure_central ~ stove_use_3 + 
                    ns(date_sphygmo, df=6) + age_baseline +
                      waist_cm + school_bi + dds_total + (1 | house_id), 
                  stove_use_data)
#summary(model_dds)
tidy_model_dds <- tidy(model_dds, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "dds")

################################################################
##### full model with all potential confounders
model_full <- lmer(pulse_pressure_central ~ stove_use_3 + 
                     ns(date_sphygmo, df=6) + age_baseline +
                       waist_cm + school_bi + dds_total + phys_act +
                       ses_materials + beds_new + 
                       (1 | house_id), stove_use_data)
#summary(model_full)
tidy_model_full <- tidy(model_full, conf.int = TRUE) %>% 
   filter(grepl('stove_use_3', term)) %>% 
    mutate(model = "full")

################################################################
######################################### stove_use_4
##### Complete-case model 
model_4level_6phases <- lmer(pulse_pressure_central ~ stove_use_4 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_4level_6phases)
tidy_model_4level_6phases <- tidy(model_4level_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "complete case")
#icc(model_4level_6phases)

################################################################
##### Missed phases model 
model_4level_5phases <- lmer(pulse_pressure_central ~ stove_use_4 + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_4level_5phases)
tidy_model_4level_5phases <- tidy(model_4level_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "missed visit")
#icc(model_4level_5phases)

################################################################
model_4level <- lmer(pulse_pressure_central ~ stove_use_4 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_4level)
#icc(model_4level)
tidy_model_4level <- tidy(model_4level, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "all data") 

################################################################
model_4level_p2_sphygmo <- lmer(pulse_pressure_central ~ stove_use_4 + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_4level_p2_sphygmo)
#icc(model_4level_p2_sphygmo)
tidy_model_4level_p2_sphygmo <- tidy(model_4level_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_4', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
######################################### stove_use_days_stack
##### Complete-case model 
model_days_6phases <- lmer(pulse_pressure_central ~ stove_use_days_stack + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_days_6phases)
tidy_model_days_6phases <- tidy(model_days_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "complete case")
#icc(model_days_6phases)

################################################################
##### Missed phases model 
model_days_5phases <- lmer(pulse_pressure_central ~ stove_use_days_stack + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_days_5phases)
tidy_model_days_5phases <- tidy(model_days_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "missed visit")
#icc(model_days_5phases)

################################################################
model_days <- lmer(pulse_pressure_central ~ stove_use_days_stack + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_days)
#icc(model_days)
tidy_model_days <- tidy(model_days, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "all data") 

################################################################
model_days_p2_sphygmo <- lmer(pulse_pressure_central ~ stove_use_days_stack + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_days_p2_sphygmo)
#icc(model_days_p2_sphygmo)
tidy_model_days_p2_sphygmo <- tidy(model_days_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_days_stack', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
######################################### stove_use_hours
##### Complete-case model 
model_hours_6phases <- lmer(pulse_pressure_central ~ stove_use_hours + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_6phases)
#summary(model_hours_6phases)
tidy_model_hours_6phases <- tidy(model_hours_6phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "complete case")
#icc(model_hours_6phases)

################################################################
##### Missed phases model 
model_hours_5phases <- lmer(pulse_pressure_central ~ stove_use_hours + 
                          ns(date_sphygmo, df=6) + age_baseline +
                          waist_cm + school_bi + (1 | house_id), 
                          r00_data_5phases)
#summary(model_hours_5phases)
tidy_model_hours_5phases <- tidy(model_hours_5phases, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "missed visit")
#icc(model_hours_5phases)

################################################################
model_hours <- lmer(pulse_pressure_central ~ stove_use_hours + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), stove_use_data)
#summary(model_hours)
#icc(model_hours)
tidy_model_hours <- tidy(model_hours, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "all data") 

################################################################
model_hours_p2_sphygmo <- lmer(pulse_pressure_central ~ stove_use_hours + 
                         ns(date_sphygmo, df=6) + 
                         waist_cm + school_bi + age_baseline +
                         (1 | house_id), r00_data_sphygmo_p2)
#summary(model_hours_p2_sphygmo)
#icc(model_hours_p2_sphygmo)
tidy_model_hours_p2_sphygmo <- tidy(model_hours_p2_sphygmo, conf.int = TRUE) %>% 
    filter(grepl('stove_use_hours', term)) %>% 
    mutate(model = "missed visit 2") 

################################################################
cpp_results_3level <- rbind(tidy_model_6phases,
                     tidy_model_5phases,
                     tidy_model_stove_use_3,
                     tidy_model_p2_sphygmo,
                     tidy_model_no_bp_meds,
                     tidy_model_phase,
                     tidy_model_season,
                     tidy_model_spline12,
                     tidy_model_bmi,
                     tidy_model_whr,
                     tidy_model_beds,
                     tidy_model_ses,
                     tidy_model_pa,
                     tidy_model_dds)

cpp_results_4level <- rbind(tidy_model_4level_6phases,
                     tidy_model_4level_5phases,
                     tidy_model_4level,
                     tidy_model_4level_p2_sphygmo)

cpp_results_days <- rbind(tidy_model_days_6phases,
                     tidy_model_days_5phases,
                     tidy_model_days,
                     tidy_model_days_p2_sphygmo)

cpp_results_hours <- rbind(tidy_model_hours_6phases,
                     tidy_model_hours_5phases,
                     tidy_model_hours,
                     tidy_model_hours_p2_sphygmo)

#kable(cpp_results)
```

## Plot model estimates - CPP and Stove Use
```{r}
plot_estimates <- cpp_results_3level %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2",
                                          "no bp meds", "visit", "season", "spline 12 df", 
                                          "bmi", "whr", "beds", "ses assets", "dds",
                                          "phys act"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_3justa+trad", "stove_use_3justa/imprvd"),
                        labels = c("justa+trad", "justa/imprvd"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with \n or without secondary stove (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(-3, -2, -1, 0, 1, 2, 3, 4)) 
plot_estimates


# stove use 4-level
plot_estimates <- cpp_results_4level %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_4justa+trad",
                                   "stove_use_4justa+imp",
                                   "stove_use_4justa"),
                        labels = c("justa+trad", "justa+imp", "justa"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with or \n without secondary stove (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 15,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5), 
                     labels = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5)) 
plot_estimates


# stove use days/month model
plot_estimates <- cpp_results_days %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_days_stackjusta+trad, 4+",
                                   "stove_use_days_stackjusta+trad, <4",
                                   "stove_use_days_stackjusta/imprvd"),
                        labels = c("justa+trad 4+ days/month", "justa+trad <4 days/month",
                                   "justa/imprvd"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove with or \n without secondary stove (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 15,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(-3, -2, -1, 0, 1, 2, 3, 4)) 
plot_estimates


# stove use hours/day model
plot_estimates <- cpp_results_hours %>%
  mutate(model = factor(model, levels = c("all data", "complete case", "missed visit", 
                                          "missed visit 2"))) %>% 
  mutate(level = factor(term, 
                        levels = c("stove_use_hourstrad, <3.5",
                                   "stove_use_hoursjusta+trad, 3.5+",
                                   "stove_use_hoursjusta+trad, <3.5",
                                   "stove_use_hoursjusta/imprvd, 3.5+",
                                   "stove_use_hoursjusta/imprvd, <3.5"),
                        labels = c("trad <3.5 hours", "justa+trad 3.5+ hours",
                                   "justa+trad <3.5 hours", "justa/imprvd 3.5+ hours",
                                   "justa/imprvd <3.5 hours"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.75), size = 4) +
  scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.75), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "AIx sensitivity analyses: area PM model") +
  labs(y = "Estimate vs traditional stove \n use 3.5+ hours/day (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .9),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-3, -2, -1, 0, 1, 2, 3, 4, 5), 
                     labels = c(-3, -2, -1, 0, 1, 2, 3, 4, 5)) 
plot_estimates


# stove use - compliance
plot_estimates <- tidy_model_compliance %>%
  mutate(level = factor(term, 
                        levels = c("stove_use_labelinconsistent",
                                   "stove_use_labelstacker"),
                        labels = c("inconsistent", "stacker"))) %>% 
  ggplot(aes(group = level, shape = level)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.75), size = 4) +
  scale_shape_manual(values = c(15, 16, 17, 18, 13, 9, 4, 8, 14, 10, 12, 7, 11)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                position = position_dodge(width = 0.75), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() + 
  labs(y = "Estimate vs compliant \n stove users (mmHg)") +
  labs(x = "") +
  theme(title = element_text(size = 16),
          legend.position = "right",
          legend.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank()) +
  scale_y_continuous(breaks = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), 
                     labels = c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10)) 
plot_estimates
```

# CPP primary model diagnostic plots - stove use
```{r}
plot(model_stove_use_3, main = "CPP and stove-use model", 
     xlab = "fitted values", ylab = "residuals")

qqnorm(residuals(model_stove_use_3), main = "CPP and stove-use model")


#aix_influential <- influence(model_apm, obs = TRUE)

#aix_cooks <- cooks.distance.estex(aix_influential, sort = TRUE)

#plot.estex(aix_influential, which = "cook")
```