---
title: "R00 Dataset Cleaning and Additions"
author: "Ethan Walker"
date: "Updated 5 May 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
```

# This markdown begins with the long (repeated by phase/visit) version of the
# R00 dataset and makes further additions and cleaning adjustments
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase_5may2020.rds") 
```

# Bonnie made changes to long version of dataset - load that and save here
```{r}
r00_new_long <- read_csv("input/r00_full_dataset_11dec2019_by.csv")

r00_full_repeated_by_phase <- r00_new_long %>% 
  # removes 6 observations for participant who wasn't assigned to a study arm
  #filter(!is.na(study_arm)) %>% 
  mutate(assigned_stove = factor(assigned_stove, levels = c("Traditional", "Justa"))) %>% 
  mutate(stove_use_3 = factor(stove_use_3, 
                                levels = c("trad", "justa+trad", "justa/imprvd"))) 
```

# Add new/updated ambient temperature and pollution data
```{r}
ambient_temp_pollution <- read_rds("output/ambient_temp_pollution.rds")

new_data <- r00_full_repeated_by_phase %>% 
  left_join(ambient_temp_pollution, by = c("house_id", "phase")) %>% 
  mutate(house_lat = house_lat.y,
         house_long = house_long.y,
         temp_datetime = temp_datetime.y,
         temp_c = temp_c.y,
         temp_lat = temp_lat.y,
         temp_long = temp_long.y,
         temp_rolling_24 = temp_rolling_24.y,
         ambient_pm = as.numeric(ambient_pm * 1000000000),
         ambient_bc = as.numeric(ambient_bc * 1000000000),
         ambient_oc = as.numeric(ambient_oc * 1000000000),
         pollution_lat = pollution_lat,
         pollution_long = pollution_long,
         pollution_datetime = pollution_datetime) %>% 
  select(-house_lat.y, -house_lat.x, -house_long.y, -house_long.x,
         -temp_datetime.y, -temp_datetime.x, -temp_c.y, -temp_c.x,
         -temp_lat.y, -temp_lat.x, -temp_long.y, -temp_long.x,
         -temp_rolling_24.y, -temp_rolling_24.x, -ambient_oc.y, -ambient_oc.x,
         -ambient_pm.y, -ambient_pm.x, -ambient_bc.y, -ambient_bc.x,
         -pollution_lat.y, -pollution_lat.x, -pollution_long.y, -pollution_long.x,
         -pollution_datetime.y, -pollution_datetime.x)
```

# Fix/re-order stove-use variables; they seemed to be ordered backwards after
# Bonnie made changes in SAS
```{r}
r00_full_long <- read_rds("output/r00_full_repeated_by_phase_5may2020.rds")

new_data <- r00_full_long %>% 
  mutate(stove_use_4 = factor(stove_use_4,
                              levels = c("trad", "justa+trad", "justa+imp", "justa"),
                              labels = c("trad", "justa+trad", "justa+imp", "justa")),
         stove_use_days_stack = factor(stove_use_days_stack,
                  levels = c("trad", "justa+trad, 4+", "justa+trad, <4", "justa/imprvd"),
                  labels = c("trad", "justa+trad, 4+", "justa+trad, <4", "justa/imprvd")),
         stove_use_hours = factor(stove_use_hours,
                  levels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+",
                             "justa+trad, <3.5", "justa/imprvd, 3.5+", "justa/imprvd, <3.5"),
                  labels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+",
                        "justa+trad, <3.5", "justa/imprvd, 3.5+", "justa/imprvd, <3.5")))
```

# Add mean within-person PM to full dataset
```{r}
r00_full_long <- read_rds("output/r00_full_repeated_by_phase_5may2020.rds") %>% 
  mutate(phase = as.factor(phase))
within_person_pm <- read_xlsx("input/mean_within_person_pm_04may2020.xlsx")

new_data <- within_person_pm %>% 
  select(-Study_Arm_r00_p2) %>% 
  group_by(house_id) %>% 
  mutate_all(as.numeric) %>% 
  pivot_longer(c("mean_log_p_twa_p1":"mean_log_a_twa_p6"), values_to = "mean_log_twa",
               names_to = "names") %>% 
  separate(names, c("names", "phase"), sep = 14) %>% 
  separate(phase, c("trash", "phase"), sep = "_p") %>% 
  pivot_wider(names_from = "names", values_from = "mean_log_twa") %>%
  select(-trash) %>% 
  ungroup() %>% 
  arrange(house_id, phase) %>% 
  right_join(r00_full_long, by = c("house_id", "phase"))
```



################ DO THESE SAVING STEPS AFTER EACH DATA ADDITION, THEN LOAD TO SERVER
# Save final, combined dataset
```{r}
write_rds(new_data, "output/r00_full_repeated_by_phase_5may2020.rds")

write_csv(new_data, "output/r00_full_repeated_by_phase_5may2020.csv", na = " ")
```

# Change AIx/CPP outliers to NA and save dataset
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase_5may2020.rds")

# USE THIS DATASET FOR AIx/CPP ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx
## This dataset is already saved -- use code above to load
r00_model_data_outliers_removed <- r00_full_long %>% 
  # removes 6 potential "outliers" with high or low AIx
  # removes 4 potential "outliers" > 75mmHg CPP
  mutate(aug_index = if_else(aug_index > 75 | aug_index < -25, 9999, aug_index)) %>% 
  mutate(pulse_pressure_central = if_else(pulse_pressure_central > 75,
                                          9999, pulse_pressure_central)) %>% 
  replace_with_na(replace = list(aug_index = 9999)) %>% 
  replace_with_na(replace = list(pulse_pressure_central = 9999)) 
write_rds(r00_model_data_outliers_removed, "output/r00_model_data_outliers_removed_5may2020.rds")
```
