---
title: "R00 Initial PM Summary Stats"
author: "Ethan Walker"
date: "April 2, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 6)
```

```{r, message=FALSE}
library(tidyverse)
library(knitr)
```

```{r, message=FALSE}
r00_full_repeated_by_phase <- read_rds("output/r00_full_repeated_by_phase.rds")
```

# Correlation matrix - Spearman
```{r}
exposure_cor <- r00_full_repeated_by_phase %>% 
  select(mean_temp, prim_sum_temp_percent_50, a_twa, p_twa) %>% 
  mutate(mean_temp_kitchen = as.numeric(mean_temp)) %>% 
  select(-mean_temp) %>% 
  filter(!is.na(mean_temp_kitchen)) %>% 
  filter(!is.na(prim_sum_temp_percent_50)) %>% 
  filter(!is.na(a_twa)) %>% 
  filter(!is.na(p_twa))

cor(exposure_cor, method = "spearman")
```

# Area PM observations per phase
```{r}
area_pm_summary <- r00_full_repeated_by_phase %>% 
  filter(!is.na(study_arm)) %>% 
  select(house_id, phase, a_twa, p_twa) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         a_twa = as.numeric(a_twa),
         p_twa = as.numeric(p_twa)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(phase) %>% 
  summarise(n_distinct(house_id))
kable(area_pm_summary, digits = 1)
```

# Personal PM observations per phase
```{r}
personal_pm_summary <- r00_full_repeated_by_phase %>% 
  filter(!is.na(study_arm)) %>% 
  select(house_id, phase, a_twa, p_twa) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         a_twa = as.numeric(a_twa),
         p_twa = as.numeric(p_twa)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(phase) %>% 
  summarise(n_distinct(house_id))
kable(personal_pm_summary, digits = 1)
```

\pagebreak 

# Area PM - total
```{r}
summary_area_pm_study_arm <- r00_full_repeated_by_phase %>% 
  select(study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>%
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "Median" = median(a_twa),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_study_arm, digits = 0)
```

# Personal PM - total
```{r}
summary_personal_pm_study_arm <- r00_full_repeated_by_phase %>% 
  select(study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>%
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "Median" = median(p_twa),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_study_arm, digits = 0)
```

\pagebreak  

# Area PM grouped by study arm
```{r}
summary_area_pm_study_arm <- r00_full_repeated_by_phase %>% 
  select(study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "Median" = median(a_twa),
            "Max" = max(a_twa),
            "IQR" = IQR(p_twa))
kable(summary_area_pm_study_arm, digits = 0)
```

# Personal PM grouped by study arm
```{r}
summary_personal_pm_study_arm <- r00_full_repeated_by_phase %>% 
  select(study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "Median" = median(p_twa),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_study_arm, digits = 0)
```

\pagebreak  

# Area PM grouped by phase and study arm
```{r}
summary_area_pm_phase <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(phase, study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "Median" = median(a_twa),
            "Max" = max(a_twa),
            "IQR" = IQR(p_twa))
kable(summary_area_pm_phase, digits = 0)
```

# Personal PM grouped by phase and study arm
```{r}
summary_personal_pm_phase <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(phase, study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "Median" = median(p_twa),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_phase, digits = 0)
```

\pagebreak  

# Area PM grouped by assigned stove type
```{r}
summary_area_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "Median" = median(a_twa),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove, digits = 0)
```

# Personal PM grouped by assigned stove type
```{r}
summary_personal_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "Median" = median(p_twa),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove, digits = 0)
```

\pagebreak  

# Area PM boxplots - all participants
```{r}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes("all participants", a_twa))
area_pm_boxplot

log_area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  mutate(log_a_twa = log(a_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes("all participants", log_a_twa)) 
log_area_pm_boxplot
```

\pagebreak  

# Personal PM boxplots - all participants
```{r}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes("all participants", p_twa))
personal_pm_boxplot

log_personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  mutate(log_p_twa = log(p_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes("all participants", log_p_twa)) 
log_personal_pm_boxplot
```

\pagebreak  

# Area PM boxplots by study arm and phase
```{r}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, a_twa)) +
  facet_wrap(~phase)
area_pm_boxplot

log_area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  mutate(log_a_twa = log(a_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, log_a_twa)) +
  facet_wrap(~phase)
log_area_pm_boxplot
```

\pagebreak  

# Personal PM boxplots by study arm and phase
```{r}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, p_twa)) +
  facet_wrap(~phase)
personal_pm_boxplot

log_personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  mutate(log_p_twa = log(p_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, log_p_twa)) +
  facet_wrap(~phase)
log_personal_pm_boxplot
```


\pagebreak  

# Area PM boxplots by assigned stove
```{r}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, a_twa)) 
area_pm_boxplot

log_area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  mutate(log_a_twa = log(a_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, log_a_twa)) 
log_area_pm_boxplot
```

\pagebreak  

# Personal PM boxplots by assigned stove
```{r}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, p_twa)) 
personal_pm_boxplot

log_personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  mutate(log_p_twa = log(p_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, log_p_twa)) 
log_personal_pm_boxplot
```

