---
title: "R00 Initial PM Summary Stats"
author: "Ethan Walker"
date: "April 2, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 6)
```

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(knitr)

jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7", "#999999")
```

```{r, message=FALSE}
# load full database
r00_full_repeated_by_phase <- read_rds("output/r00_full_repeated_by_phase_5may2020.rds") 

%>% 
  select(date_sphygmo)

#r00_model_data_outliers_removed <- read_rds("output/r00_model_data_outliers_removed.RDS")

# Dataset for participants who have AIx data for all 6 Phases (113 participants)
r00_data_6phases <- r00_full_repeated_by_phase %>% 
  filter(!is.na(assigned_stove)) %>% 
  group_by(house_id) %>% 
  #create new var to be able to filter for participants that completed 6 phases
  mutate(phase_complete = if_else(!is.na(aug_index), 1, 0)) %>% 
  filter(sum(phase_complete) == 6) %>% 
  ungroup()

# Dataset for participants who did not miss phase 2
r00_model_data_phase2 <- r00_full_repeated_by_phase %>% 
  filter(!is.na(assigned_stove)) %>% 
  mutate(phase2 = 1) %>% 
  mutate(phase2 = if_else(phase == 2 & is.na(aug_index), 0, phase2)) %>%  
  group_by(house_id) %>% 
  filter(sum(phase2) == 6) %>%
  ungroup() 
```

# Correlation matrix - Spearman
```{r}
# also try adding: mean_temp, prim_sum_temp_percent_50, 
exposure_cor <- r00_full_repeated_by_phase %>% 
  select(a_twa, p_twa, kitchen_temp, sys_bp_periph) %>% 
  filter(!is.na(a_twa)) %>% 
  filter(!is.na(p_twa)) %>% 
  filter(!is.na(kitchen_temp)) %>% 
  filter(!is.na(sys_bp_periph))

cor(exposure_cor, method = "spearman")
```

# Area PM observations per phase
```{r}
area_pm_summary <- r00_full_repeated_by_phase %>% 
  filter(!is.na(study_arm)) %>% 
  select(house_id, phase, a_twa, p_twa) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         a_twa = as.numeric(a_twa),
         p_twa = as.numeric(p_twa)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(phase) %>% 
  summarise(n_distinct(house_id))
kable(area_pm_summary, digits = 1)
```

# Personal PM observations per phase
```{r}
personal_pm_summary <- r00_full_repeated_by_phase %>% 
  filter(!is.na(study_arm)) %>% 
  select(house_id, phase, a_twa, p_twa) %>% 
  mutate(house_id = as.factor(house_id),
         phase = as.factor(phase),
         a_twa = as.numeric(a_twa),
         p_twa = as.numeric(p_twa)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(phase) %>% 
  summarise(n_distinct(house_id))
kable(personal_pm_summary, digits = 1)
```

\pagebreak 

# Area PM - total
```{r}
summary_area_pm_study_arm <- r00_full_repeated_by_phase %>% 
  select(study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>%
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_study_arm, digits = 0)
```

# Personal PM - total
```{r}
summary_personal_pm_study_arm <- r00_model_data_phase2 %>% 
  select(study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>%
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_study_arm, digits = 0)
```

\pagebreak  

# Area PM grouped by study arm - phase 1
```{r}
summary_area_pm_study_arm <- r00_full_repeated_by_phase %>% 
  filter(phase == 1) %>% 
  select(study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_study_arm, digits = 0)
```

# Personal PM grouped by study arm - phase 1
```{r}
summary_personal_pm_study_arm <- r00_full_repeated_by_phase %>% 
  filter(phase == 1) %>% 
  select(study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_study_arm, digits = 0)
```

\pagebreak  

# Area PM by season
```{r}
summary_area_pm_season <- r00_full_repeated_by_phase %>% 
  ungroup() %>% 
  #filter(phase == 1) %>% 
  select(season, a_twa) %>% 
  filter(!is.na(season)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(season) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_season, digits = 0)
```

# Personal PM by season
```{r}
summary_personal_pm_season <- r00_full_repeated_by_phase %>%  
  ungroup() %>% 
  #filter(phase == 1) %>% 
  select(season, p_twa) %>% 
  filter(!is.na(season)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(season) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_season, digits = 0)
```

\pagebreak  

# Area PM grouped by phase and study arm
```{r}
summary_area_pm_phase <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(phase, study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_phase, digits = 0)
```

# Personal PM grouped by phase and study arm
```{r}
summary_personal_pm_phase <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(phase, study_arm) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_phase, digits = 0)
```

\pagebreak  

# Area PM grouped by assigned stove type
```{r}
summary_area_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove, digits = 0)

summary_area_pm_stove <- r00_model_data_phase2 %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove, digits = 0)
```

# Personal PM grouped by assigned stove type
```{r}
summary_personal_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove, digits = 0)

summary_personal_pm_stove <- r00_model_data_phase2 %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove, digits = 0)
```

\pagebreak 

# Area PM grouped by assigned stove type and season
```{r}
summary_area_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa, season) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  filter(!is.na(season)) %>% 
  group_by(season, assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "Min" = min(a_twa), 
            "25th" = quantile(a_twa, c(.25)),
            "Median" = median(a_twa),
            "75th" = quantile(a_twa, c(.75)),
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove, digits = 0)
```

# Personal PM grouped by assigned stove type and season
```{r}
summary_personal_pm_stove <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa, season) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>%  
  filter(!is.na(season)) %>% 
  group_by(season, assigned_stove) %>% 
  summarise("n" = n(),
            "Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "Min" = min(p_twa), 
            "25th" = quantile(p_twa, c(.25)),
            "Median" = median(p_twa),
            "75th" = quantile(p_twa, c(.75)),
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove, digits = 0)
```

\pagebreak 

# Area PM grouped by stove use
```{r}
summary_area_pm_stove_use <- r00_full_repeated_by_phase %>% 
  select(stove_use_3, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(stove_use_3) %>% 
  summarise("Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "n" = n(),
            "25th" = quantile(a_twa, c(.25)),
            "75th" = quantile(a_twa, c(.75)),
            "Median" = median(a_twa),
            "Min" = min(a_twa), 
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove_use, digits = 0)

summary_area_pm_stove_use <- r00_model_data_phase2 %>% 
  select(stove_use_3, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  group_by(stove_use_3) %>% 
  summarise("Mean" = mean(a_twa),
            "SD" = sd(a_twa), 
            "n" = n(),
            "25th" = quantile(a_twa, c(.25)),
            "75th" = quantile(a_twa, c(.75)),
            "Median" = median(a_twa),
            "Min" = min(a_twa), 
            "Max" = max(a_twa),
            "IQR" = IQR(a_twa))
kable(summary_area_pm_stove_use, digits = 0)
```

# Personal PM grouped by stove use
```{r}
summary_personal_pm_stove_use <- r00_full_repeated_by_phase %>% 
  select(stove_use_3, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(stove_use_3) %>% 
  summarise("Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "n" = n(),
            "25th" = quantile(p_twa, c(.25)),
            "75th" = quantile(p_twa, c(.75)),
            "Median" = median(p_twa),
            "Min" = min(p_twa), 
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove_use, digits = 0)

summary_personal_pm_stove_use <- r00_model_data_phase2 %>% 
  select(stove_use_3, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  group_by(stove_use_3) %>% 
  summarise("Mean" = mean(p_twa),
            "SD" = sd(p_twa), 
            "n" = n(),
            "25th" = quantile(p_twa, c(.25)),
            "75th" = quantile(p_twa, c(.75)),
            "Median" = median(p_twa),
            "Min" = min(p_twa), 
            "Max" = max(p_twa),
            "IQR" = IQR(p_twa))
kable(summary_personal_pm_stove_use, digits = 0)
```

\pagebreak 

# Area PM boxplots - all participants
```{r, fig.height=4, fig.width=8}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa, assigned_stove, stove_use_3) %>% 
  mutate(phase = factor(phase, levels = c(1,2,3,4,5,6),
                        labels = c("Visit 1", "Visit 2",
                                   "Visit 3", "Visit 4",
                                   "Visit 5", "Visit 6"))) %>% 
  filter(!is.na(assigned_stove)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot(aes(1, a_twa)) +
    geom_boxplot(aes(assigned_stove, a_twa, fill = assigned_stove, size = 1), 
                 lwd = 1.2, colour = "black", 
                 fatten = 1, outlier.size = 1.5, width = 0.75) +
    #stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    scale_y_log10(breaks = c(1, 10, 100, 1000, 10000),
                  labels = c(1, 10, 100, 1000, 10000),
                  limits = c(1, 10000)) +
    theme_minimal() +
    scale_fill_manual(values = cbPalette) +
    ylab(expression(paste("24-hour Kitchen PM "[2.5], " (", mu, g/m^3, ")"))) +
    labs(x = " ", fill = "Assigned Stove: ") +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_text(size = 16, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid = element_blank(),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.line.x.top = element_line(colour = "black", size = 1.2),
          axis.ticks = element_blank()) +
    facet_grid(~phase)
area_pm_boxplot

ggsave("kitchen_pm_boxplots.jpeg", height = 4, width = 8)
```

\pagebreak  

# Personal PM boxplots - all participants
```{r, fig.height=4, fig.width=8}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa, assigned_stove, stove_use_3) %>% 
  mutate(phase = factor(phase, levels = c(1,2,3,4,5,6),
                        labels = c("Visit 1", "Visit 2",
                                   "Visit 3", "Visit 4",
                                   "Visit 5", "Visit 6"))) %>% 
  filter(!is.na(assigned_stove)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot(aes(1, p_twa)) +
    geom_boxplot(aes(assigned_stove, p_twa, fill = assigned_stove, size = 1), 
                 lwd = 1.2, colour = "black", 
                 fatten = 1, outlier.size = 1.5, width = 0.75) +
    #stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    scale_y_log10(breaks = c(1, 10, 100, 1000, 10000),
                  labels = c(1, 10, 100, 1000, 10000),
                  limits = c(1, 10000)) +
    theme_minimal() +
    scale_fill_manual(values = cbPalette) +
    ylab(expression(paste("24-hour Personal PM "[2.5], " (", mu, g/m^3, ")"))) +
    labs(x = " ", fill = "Assigned Stove: ") +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_text(size = 16, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          legend.position = "top",
          panel.grid = element_blank(),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.line.x.top = element_line(colour = "black", size = 1.2),
          axis.ticks = element_blank()) +
    facet_grid(~phase)
personal_pm_boxplot

ggsave("personal_pm_boxplots.jpeg", height = 4, width = 8)
```

\pagebreak  

# Area PM boxplots by study arm and phase
```{r}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, a_twa)) +
  facet_wrap(~phase)
area_pm_boxplot

log_area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, a_twa) %>% 
  mutate(log_a_twa = log(a_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, log_a_twa)) +
  facet_wrap(~phase)
log_area_pm_boxplot
```

\pagebreak  

# Personal PM boxplots by study arm and phase
```{r}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(study_arm, p_twa)) +
  facet_wrap(~phase)
personal_pm_boxplot

log_personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(phase, assigned_stove, p_twa) %>% 
  mutate(log_p_twa = log(p_twa)) %>% 
  filter(!is.na(assigned_stove)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(1, log_p_twa, fill = assigned_stove)) +
  facet_wrap(~phase)
log_personal_pm_boxplot
```


\pagebreak  

# Area PM boxplots by assigned stove
```{r}
area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, a_twa)) 
area_pm_boxplot

log_area_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, a_twa) %>% 
  mutate(log_a_twa = log(a_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(a_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, log_a_twa)) 
log_area_pm_boxplot
```

\pagebreak  

# Personal PM boxplots by assigned stove
```{r}
personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, p_twa)) 
personal_pm_boxplot

log_personal_pm_boxplot <- r00_full_repeated_by_phase %>% 
  select(assigned_stove, study_arm, p_twa) %>% 
  mutate(log_p_twa = log(p_twa)) %>% 
  filter(!is.na(study_arm)) %>% 
  filter(!is.na(p_twa)) %>% 
  ggplot() +
  geom_boxplot(aes(assigned_stove, log_p_twa)) 
log_personal_pm_boxplot
```

