---
title: "Data Cleaning"
author: "Ethan Walker"
date: "Updated 9 Oct 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
```

# This RMD starts with Bonnie's health dataset in wide format,
## then converts it to long format (repeated by phase),
## then binds it to sphygmocor, SUMs, and exposure datasets,
## then creates new variables for analysis,
## then saves the final database as RDS and CSV files.

```{r, message=FALSE}
# Load data
r00_full_wide <- read_xlsx("input/r00_health_wide_dataset_09July2019_by.xlsx")

#r00_full_wide <- readRDS("output/r00_full_wide.rds")
```

##### Convert Dataset from Wide to Long #####
```{r}
r00_full_long <- r00_full_wide %>% 
  #taking out duplicate variables
  select(-sys_bp_periph_r00_p2, -dia_bp_periph_r00_p2) %>% 
  #creating new variables for phases 2-6 if it was only collected at phase 1
  mutate(electricity_r00_p2 = electricity_r00_p1, 
         electricity_r00_p3 = electricity_r00_p1, 
         electricity_r00_p4 = electricity_r00_p1, 
         electricity_r00_p5 = electricity_r00_p1, 
         electricity_r00_p6 = electricity_r00_p1) %>%
  mutate(school_bi_r00_p2 = school_bi_r00_p1, 
         school_bi_r00_p3 = school_bi_r00_p1, 
         school_bi_r00_p4 = school_bi_r00_p1, 
         school_bi_r00_p5 = school_bi_r00_p1, 
         school_bi_r00_p6 = school_bi_r00_p1) %>%
  mutate(community_cat_r00_p2 = community_cat_r00_p1, 
         community_cat_r00_p3 = community_cat_r00_p1, 
         community_cat_r00_p4 = community_cat_r00_p1, 
         community_cat_r00_p5 = community_cat_r00_p1, 
         community_cat_r00_p6 = community_cat_r00_p1) %>%
  mutate(birth_year_r00_p2 = birth_year_r00_p1, 
         birth_year_r00_p3 = birth_year_r00_p1, 
         birth_year_r00_p4 = birth_year_r00_p1, 
         birth_year_r00_p5 = birth_year_r00_p1, 
         birth_year_r00_p6 = birth_year_r00_p1) %>%
  rename(beds_new_r00_p1 = beds_new) %>% 
  mutate(beds_new_r00_p2 = beds_new_r00_p1, 
         beds_new_r00_p3 = beds_new_r00_p1, 
         beds_new_r00_p4 = beds_new_r00_p1, 
         beds_new_r00_p5 = beds_new_r00_p1, 
         beds_new_r00_p6 = beds_new_r00_p1) %>%
  mutate(indigenous_r00_p2 = indigenous_r00_p1, 
         indigenous_r00_p3 = indigenous_r00_p1, 
         indigenous_r00_p4 = indigenous_r00_p1, 
         indigenous_r00_p5 = indigenous_r00_p1, 
         indigenous_r00_p6 = indigenous_r00_p1) %>%
  mutate(school_self_r00_p2 = school_self_r00_p1, 
         school_self_r00_p3 = school_self_r00_p1, 
         school_self_r00_p4 = school_self_r00_p1, 
         school_self_r00_p5 = school_self_r00_p1, 
         school_self_r00_p6 = school_self_r00_p1) %>%
  mutate(elevation_r00_p2 = elevation_r00_p1, 
         elevation_r00_p3 = elevation_r00_p1, 
         elevation_r00_p4 = elevation_r00_p1, 
         elevation_r00_p5 = elevation_r00_p1, 
         elevation_r00_p6 = elevation_r00_p1) %>% 
  mutate(sex_r00_p2 = sex_r00_p1, 
         sex_r00_p3 = sex_r00_p1, 
         sex_r00_p4 = sex_r00_p1, 
         sex_r00_p5 = sex_r00_p1, 
         sex_r00_p6 = sex_r00_p1) %>% 
  mutate(pers_info_r00_p2 = pers_info_r00_p1, 
         pers_info_r00_p3 = pers_info_r00_p1, 
         pers_info_r00_p4 = pers_info_r00_p1, 
         pers_info_r00_p5 = pers_info_r00_p1, 
         pers_info_r00_p6 = pers_info_r00_p1) %>% 
  rename(ses_materials_r00_p1 = ses_materials) %>% 
  mutate(ses_materials_r00_p2 = ses_materials_r00_p1, 
         ses_materials_r00_p3 = ses_materials_r00_p1, 
         ses_materials_r00_p4 = ses_materials_r00_p1, 
         ses_materials_r00_p5 = ses_materials_r00_p1, 
         ses_materials_r00_p6 = ses_materials_r00_p1) %>%
  mutate(study_arm_r00_p1 = Study_Arm_r00_p2, 
         study_arm_r00_p2 = Study_Arm_r00_p2,
         study_arm_r00_p3 = Study_Arm_r00_p2, 
         study_arm_r00_p4 = Study_Arm_r00_p2, 
         study_arm_r00_p5 = Study_Arm_r00_p2, 
         study_arm_r00_p6 = Study_Arm_r00_p2) %>% 
  mutate(age_baseline_r00_p2 = age_baseline_r00_p1, 
         age_baseline_r00_p3 = age_baseline_r00_p1,
         age_baseline_r00_p4 = age_baseline_r00_p1, 
         age_baseline_r00_p5 = age_baseline_r00_p1, 
         age_baseline_r00_p6 = age_baseline_r00_p1) %>% 
  select(-Study_Arm_r00_p2) %>% 
  #transform data to long format with only 3 columns
  gather(key = "variable", value = "value", -house_id) %>% 
  #arrange data by house_id, descending
  arrange(house_id)

r00_full_repeated_by_phase <- r00_full_long %>%
  #this variable has no corresponding phase
  #renaming to phase 1 so it spreads below
  mutate(variable = if_else(variable == "group", 
                            "group_r00_p1", variable)) %>%
  #separate variable to create new phase column
  separate(variable, c("variable", "phase"), sep = "_r00_p") %>%
  #replace "." with "99999" and then change to "na"
  mutate(value = if_else(value == ".", "99999", value)) %>% 
  replace_with_na(replace = list(value = 99999)) %>% 
  #separate phase and "new", then attach "new" to variable
  separate(phase, c("phase", "new"), sep = "_") %>% 
  unite("variable", c("variable", "new")) %>% 
  #remove NA from end of variables that was added above
  separate(variable, c("variable", "trash"), sep = "_NA") %>% 
  select(-"trash") %>% 
  #spread out into columns, grouped by house_id and phase
  spread(key = "variable", value = "value") %>% 
  arrange(house_id)

# Check number of house_id
n_distinct(r00_full_repeated_by_phase$house_id)
```

# Combine with cleaned Sphygmocor dataset (from r00_initial_sphygmocor_cleaning.rmd)
```{r}
r00_pwa <- readRDS("output/r00_sphygmocor_pwa.rds")

  
r00_joined_1 <- r00_full_repeated_by_phase %>% 
  #create new date var (tidy format) to merge with sphygmocor dataset
  mutate(date_new = date) %>% 
  separate(date_new, c("day_week", "month", "day", "time", "utc", "year"), sep = " ") %>% 
  unite(date_new, c("year", "month", "day"), sep = "") %>% 
  mutate(date_setup = ymd(date_new)) %>% 
  mutate(date_sphygmo = ymd(date_new) + days(1)) %>% 
  #fix incorrect dates described in "r00_initial_sphygmocor_cleaning" so merge will line up 
  mutate(date_sphygmo = if_else(house_id == "CAC007" & date_sphygmo == "2016-09-22",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "CER064" & date_sphygmo == "2017-04-11",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "HOR041" & date_sphygmo == "2016-09-08",
                               date_sphygmo + days(2), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "OLO007" & date_sphygmo == "2016-10-21",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "PER052" & date_sphygmo == "2016-11-18",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "QDL012" & date_sphygmo == "2017-04-27",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "ZAC014" & date_sphygmo == "2015-09-05",
                               date_sphygmo + days(2), date_sphygmo)) %>% 
  mutate(date_sphygmo = if_else(house_id == "ZAC027" & date_sphygmo == "2015-09-10",
                               date_sphygmo + days(1), date_sphygmo)) %>% 
  select(-"day_week", -"time", -"utc", -"date_new") %>% 
  #join with cleaned pwa dataset
  left_join(r00_pwa, by = c("house_id", "date_sphygmo")) 

```

# Combine with cleaned SUMS dataset (from r00_sums_data_cleaning.rmd)
```{r}
r00_sums_full_dataset <- readRDS("output/r00_sums_full_dataset.rds")

r00_joined_2 <- r00_joined_1 %>% 
  left_join(r00_sums_full_dataset, by = c("house_id", "phase"))

```

# Combine with old exposure dataset (from r00_exposure_wide_to_long.rmd)
#### Outdated step - DO NOT USE
```{r}
# This is old exposure data that has already been added to the wide database
# Don't do this step!
#r00_exposure_repeated_by_phase <- read_rds("output/r00_exposure_repeated_by_phase.rds")

#r00_joined_3 <- r00_joined_2 %>% 
 # full_join(r00_exposure_repeated_by_phase, by = c("house_id", "phase")) 
```

# Combine with Megan's new PM2.5 dataset (from r00_pm_database_final.rmd)
```{r}
r00_pm_final <- read_rds("output/r00_pm_final.rds") %>% 
  # select these vars out - already in the wide database
  select(-a_twa, -p_twa)

r00_joined_3 <- r00_joined_2 %>% 
  full_join(r00_pm_final, by = c("house_id", "phase")) 

```

# Create new variables to use in analyses
```{r}
r00_final_long <- r00_joined_3 %>% 
  ##### Fix incorrect height/bmi in database #####
  mutate(height = as.numeric(height)) %>% 
  mutate(weight = as.numeric(weight)) %>% 
  mutate(height = if_else(phase == 6 & house_id == "CER009", 57.0, height)) %>% 
  mutate(bmi = (weight*0.453592)/((height*0.0254)^2)) %>% 
  mutate(sys_bp_central = as.numeric(sys_bp_central),
         dia_bp_central = as.numeric(dia_bp_central),
         sys_bp_periph = as.numeric(sys_bp_periph),
         dia_bp_periph = as.numeric(dia_bp_periph),
         aug_index = as.numeric(aug_index),
         aug_index_75 = as.numeric(aug_index_75),
         pulse_pressure_periph = as.numeric(pulse_pressure_periph),
         pulse_pressure_central = as.numeric(pulse_pressure_central),
         hr = as.numeric(hr),
         bmi = as.numeric(bmi),
         whr = as.numeric(whr),
         waist = as.numeric(waist),
         waist_cm = as.numeric(waist * 2.54),
         dds_total = as.numeric(dds_total),
         phys_act = as.numeric(phys_act),
         beds_new = as.numeric(beds_new),
         ses_materials = as.numeric(ses_materials),
         school_self = as.numeric(school_self),
         age_baseline = as.numeric(age_baseline),
         hba1c = as.numeric(hba1c),
         hdl = as.numeric(hdl),
         triglycerides = as.numeric(triglycerides))%>% 
  mutate(phase = as.factor(phase),
         season = as.factor(season),
         house_id = as.factor(house_id),
         school_bi = as.factor(school_bi),
         whr_cat = as.factor(whr_cat)) %>%
  mutate(salt_cat = if_else(salt >=8, "Salt 8+", "Salt < 8")) %>% 
  mutate(sugar_cat = if_else(sugar >=4, "Sugar 4+", "Sugar < 4")) %>% 
  mutate(manteca_cat = if_else(manteca >=7, "Manteca 7+", "Manteca < 7")) %>% 
  mutate(assigned_stove = factor(assigned_stove, levels = c(0, 1), 
                                 labels = c("Traditional", "Justa"))) %>% 
  #split waist at 80cm
  mutate(waist_cat = if_else(waist_cm < 79.9, "waist < 80cm", "waist >= 80cm")) %>%
  mutate(waist_cat = as.factor(waist_cat)) %>% 
  #split age at 40
  mutate(age_cat_40 = if_else(age_baseline < 39.9, "age < 40", "age >= 40")) %>% 
  mutate(age_cat_40 = as.factor(age_cat_40)) %>% 
  #split bmi at 25
  mutate(bmi_cat = if_else(bmi < 24.99, "bmi < 25", "bmi >= 25")) %>% 
  mutate(bmi_cat = as.factor(bmi_cat)) %>%
  #split a1c at 5.7
  mutate(hba1c_cat = if_else(hba1c < 5.69, "a1c < 5.7", "a1c >=5.7")) %>% 
  mutate(hba1c_cat = as.factor(hba1c_cat)) %>%
  #bp normal/high
  mutate(bp_cat = if_else(sys_bp_periph < 120.9 & dia_bp_periph < 80.9, 
                          "bp norm", "bp high")) %>% 
  mutate(bp_cat = factor(bp_cat, levels = c("bp norm", "bp high"))) %>% 
  mutate(ses_cat_2 = if_else(ses_materials > 2, "SES 3+", "SES < 3")) %>% 
  mutate(bpp_cat = if_else(beds_new >=0.5, "BPP 0.5+", "BPP < 0.5")) %>% 
  mutate(dds_cat = if_else(dds_total >=6, "DDS 6+", "DDS < 6")) %>% 
  mutate(phys_act_cat = if_else(phys_act >=300, "METS 300+", "METS < 300")) %>% 
  #new metsyn variable
  mutate(sys_bp_ms = if_else(sys_bp_periph >= 130, 1, 0),
         dia_bp_ms = if_else(dia_bp_periph >= 85, 1, 0),
         trigs_ms = if_else(triglycerides > 200, 1, 0),
         hdl_ms = if_else(hdl < 50, 1, 0),
         a1c_ms = if_else(hba1c > 5.6, 1, 0),
         waist_ms = if_else(waist_cm > 80, 1, 0)) %>% 
  mutate(ms_sum = (sys_bp_ms + dia_bp_ms + trigs_ms + hdl_ms + a1c_ms)) %>% 
  mutate(met_syn = if_else(waist_ms == 1 & ms_sum > 1, "met syn", "no met syn")) %>% 
  mutate(met_syn = factor(met_syn, levels = c("no met syn", "met syn"))) %>% 
  #log transforming personal and area pm2.5
  mutate(a_twa = as.numeric(a_twa)) %>% 
  mutate(p_twa = as.numeric(p_twa)) %>% 
  mutate(log_a_twa = as.numeric(log(a_twa))) %>% 
  mutate(log_p_twa = as.numeric(log(p_twa))) %>% 
  # Add dichotomous variable for secondary stove use (50C)
  mutate(sec_stove_sums = if_else(sec_sum_event_count_50 > 0, 1, 0)) %>% 
  #create new stove use variable based on actual_stove_use
  mutate(stove_use = as.numeric(actual_stove_use)) %>% 
  mutate(stove_use = if_else(phase == 1 | phase == 2, 3, stove_use)) %>% 
  mutate(stove_use_4 = factor(stove_use, levels = c(0,1,2,3),
                              labels = c("justa", "justa+imp", "justa+trad", "trad"))) %>% 
  mutate(stove_use_4 = factor(stove_use_4, 
                              levels = c("trad", "justa+trad", "justa+imp", "justa"))) %>% 
  mutate(stove_use_3 = if_else(stove_use == 0, 1, stove_use)) %>% 
  mutate(stove_use_3 = factor(stove_use_3, levels = c(1,2,3),
                            labels = c("justa/imprvd", "justa+trad", "trad"))) %>% 
  mutate(stove_use_3 = factor(stove_use_3, 
                            levels = c("trad", "justa+trad", "justa/imprvd"))) %>% 
  mutate(stove_use = factor(stove_use, 
                            levels = c(0,1,2,3),
                            labels = c(3,2,1,0))) %>% 
  mutate(stove_use = factor(stove_use, 
                            levels = c(0,1,2,3))) %>% 
  # splitting days_sec at <4 and 4+
  mutate(days_sec_4 = if_else(days_sec < 4, 0, 1)) %>%
  mutate(days_sec_4 = factor(days_sec_4, levels = c(0,1), labels = c("<4", "4+"))) %>%
  # splitting hours_primary at <3.5 and 3.5+
  mutate(hours_primary_3.5 = if_else(hours_primary < 3.5, 0, 1)) %>%
  mutate(hours_primary_3.5 = factor(hours_primary_3.5, 
                                    levels = c(0,1), labels = c("<3.5", "3.5+"))) %>%
  # mutating stove_use_3 to character for use in if_else statement
  mutate(stove_use_3 = as.character(stove_use_3)) %>% 
  # new variable incorporating days/month of secondary stove use (<4 vs 4+) 
  # only doing this for justa+trad levels
  ## because only 24 people reported 4+ days improved secondary stove use with Justa
  ## and this data wasn't available in phase 1
  mutate(stove_use_days_stack = 
         if_else(stove_use_3 == "justa+trad" & days_sec_4 == "4+",
                 "justa+trad, 4+", stove_use_3)) %>% 
  mutate(stove_use_days_stack = 
           factor(stove_use_days_stack,
                  levels = c("justa/imprvd", "justa+trad", 
                             "justa+trad, 4+", "trad"),
                  labels = c("justa/imprvd", "justa+trad, <4", 
                             "justa+trad, 4+", "trad"))) %>%
  # reorder new var so traditional is reference
  mutate(stove_use_days_stack = 
           factor(stove_use_days_stack,
                  levels = c("trad", "justa+trad, 4+", 
                             "justa+trad, <4", "justa/imprvd"))) %>%
  # new variable incorporating hours/day of primary stove use (<3.5 vs 3.5+) 
  mutate(stove_use_hours = 
         if_else(stove_use_3 == "justa+trad" & hours_primary_3.5 == "3.5+",
                 "justa+trad, 3.5+", stove_use_3)) %>% 
  mutate(stove_use_hours = 
         if_else(stove_use_hours == "trad" & hours_primary_3.5 == "3.5+",
                 "trad, 3.5+", stove_use_hours)) %>% 
  mutate(stove_use_hours = 
         if_else(stove_use_hours == "justa/imprvd" & hours_primary_3.5 == "3.5+",
                 "justa/imprvd, 3.5+", stove_use_hours)) %>% 
  mutate(stove_use_hours = 
           factor(stove_use_hours,
                  levels = c("justa/imprvd", "justa/imprvd, 3.5+", "justa+trad", 
                             "justa+trad, 3.5+", "trad", "trad, 3.5+"),
                  labels = c("justa/imprvd, <3.5", "justa/imprvd, 3.5+", "justa+trad, <3.5", 
                             "justa+trad, 3.5+", "trad, <3.5", "trad, 3.5+"))) %>%
  # reorder new var so traditional 3.5+ hours is reference
  mutate(stove_use_hours = 
           factor(stove_use_hours,
                  levels = c("trad, 3.5+", "trad, <3.5", "justa+trad, 3.5+", 
                             "justa+trad, <3.5", "justa/imprvd, 3.5+", 
                             "justa/imprvd, <3.5"))) %>%
  mutate(stove_use_3 = factor(stove_use_3, 
                            levels = c("trad", "justa+trad", "justa/imprvd"))) %>% 
  mutate(pregnant_new = if_else(house_id == "ANT011" & phase == 2, 1, 0),
         pregnant_new = if_else(house_id == "CAC034" & phase == 5, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CAC060" & phase == 2, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CAC062" & phase == 4, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CAC062" & phase == 5, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CER010" & phase == 3, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CER023" & phase == 4, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CER023" & phase == 5, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CER042" & phase == 2, 1, pregnant_new),
         pregnant_new = if_else(house_id == "CER042" & phase == 5, 1, pregnant_new),
         pregnant_new = if_else(house_id == "HOR071" & phase == 4, 1, pregnant_new),
         pregnant_new = if_else(house_id == "MOM026" & phase == 2, 1, pregnant_new),
         pregnant_new = if_else(house_id == "MOM062" & phase == 3, 1, pregnant_new),
         pregnant_new = if_else(house_id == "MOM062" & phase == 4, 1, pregnant_new),
         pregnant_new = if_else(house_id == "OLO102" & phase == 2, 1, pregnant_new),
         pregnant_new = if_else(house_id == "PER067" & phase == 5, 1, pregnant_new),
         pregnant_new = if_else(house_id == "PER067" & phase == 6, 1, pregnant_new),
         pregnant_new = if_else(house_id == "QDL018" & phase == 2, 1, pregnant_new),
         pregnant_new = if_else(house_id == "QDL027" & phase == 3, 1, pregnant_new),
         pregnant_new = if_else(house_id == "ZAC095" & phase == 3, 1, pregnant_new)) %>% 
  # format data
  separate(child_born, c("day_week", "month", "day", "time", "utc", "year"), sep = " ") %>% 
  unite(date_new, c("year", "month", "day"), sep = "") %>% 
  mutate(child_born_date = ymd(date_new)) %>% 
  select(-"day_week", -"time", -"utc", -"date_new") %>% 
  # difference between date of health assessment and last child born
  mutate(date_diff = date_sphygmo - child_born_date) %>% 
  # if dates are less than 6 mo apart, they were pregnant for previous session
  mutate(pregnant2 = if_else(date_diff < 182, 1, 0)) %>% 
  group_by(house_id) %>% 
  mutate(pregnant3 = lead(pregnant2)) %>% 
  # check to see if this method of assessing pregnancy matches with our records
  ## 2 additional instances of pregnancy found by this method
  ## adding to pregnancy_new, below
  mutate(pregnant_test = if_else(pregnant_new == pregnant3, 1, 0)) %>%
  mutate(pregnant_new = if_else(house_id == "OLO093" & phase == 4, 1, pregnant_new),
         pregnant_new = if_else(house_id == "ZAC098" & phase == 3, 1, pregnant_new)) %>% 
  mutate(pregnant_previous = lag(pregnant_new)) %>%
  select(-pregnant2, -pregnant3, -pregnant_test, -date_diff) %>% 
  ungroup()
```

# Join inflammatory markers with full dataset
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds") 
# load inflammatory dataset
inflammatory_data <- read_xlsx("input/r00_dbs_data_20191009.xlsx")

inflammatory_data_clean <- inflammatory_data %>% 
  # rename variables
  mutate(house_id = as.factor(X__1),
         phase = as.factor(X__2),
         il1b_dbs_a = as.numeric(X__3),
         il6_dbs_a = as.numeric(X__4),
         il8_dbs_a = as.numeric(X__5),
         tnfa_dbs_a = as.numeric(X__6),
         tnfa_2_dbs_a = as.numeric(Repeated),
         crp_dbs_a = as.numeric(X__7)) %>% 
  # separate phase to remove "p"
  separate(phase, c("p", "phase"), sep = "p") %>% 
  # select new variables/discard old variables
  select(house_id, phase, il1b_dbs_a, il6_dbs_a, il8_dbs_a, tnfa_dbs_a, 
         tnfa_2_dbs_a, crp_dbs_a) %>% 
  # filter out invalid rows for "house_id"
  filter(house_id != "ID") %>% 
  # fix phases that had more than just phase number
  separate(phase, c("phase", "trash"), sep = " ") %>%
  mutate(phase = if_else(phase == "5****", "5", phase)) %>% 
  select(-trash) %>% 
  # replace "NaN" with "NA" throughout dataset
  replace_with_na(replace = list(il1b_dbs_a = "NaN")) %>% 
  replace_with_na(replace = list(il6_dbs_a = "NaN")) %>%
  replace_with_na(replace = list(il8_dbs_a = "NaN")) %>%
  replace_with_na(replace = list(tnfa_dbs_a = "NaN")) %>%
  replace_with_na(replace = list(tnfa_2_dbs_a = "NaN")) %>%
  replace_with_na(replace = list(crp_dbs_a = "NaN"))
  

full_inflammatory_joined <- r00_full_long %>% 
  left_join(inflammatory_data_clean, by = c("house_id", "phase"))
##### Save as final combined dataset in chunk below #####
```

# Create new variables for existing database
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")

new_vars <- r00_full_long %>% 
  # new BP vars that join Sphygmo and Nurse BP values
  mutate(sys_bp_periph = as.character(sys_bp_periph)) %>% 
  mutate(sys_bp_joined = if_else(is.na(sys_bp_periph), sys_bp_final_nurse, sys_bp_periph)) %>% 
  mutate(sys_bp_periph = as.numeric(sys_bp_periph),
         sys_bp_final_nurse = as.numeric(sys_bp_final_nurse),
         sys_bp_joined = as.numeric(sys_bp_joined)) %>% 
  mutate(dia_bp_periph = as.character(dia_bp_periph)) %>% 
  mutate(dia_bp_joined = if_else(is.na(dia_bp_periph), dia_bp_final_nurse, dia_bp_periph)) %>% 
  mutate(dia_bp_periph = as.numeric(dia_bp_periph),
         dia_bp_final_nurse = as.numeric(dia_bp_final_nurse),
         dia_bp_joined = as.numeric(dia_bp_joined)) %>% 
  #create new indicator vars to be able to filter for participants who completed 6 phases
  group_by(house_id) %>% 
  mutate(phase_complete_aix = if_else(!is.na(aug_index), 1, 0),
         complete_case_aix = if_else(sum(phase_complete_aix) == 6, 1, 0),
         phase_complete_cpp = if_else(!is.na(pulse_pressure_central), 1, 0),
         complete_case_cpp = if_else(sum(phase_complete_cpp) == 6, 1, 0),
         phase_complete_sbp = if_else(!is.na(sys_bp_periph), 1, 0),
         complete_case_sbp = if_else(sum(phase_complete_sbp) == 6, 1, 0),
         phase_complete_dbp = if_else(!is.na(dia_bp_periph), 1, 0),
         complete_case_dbp = if_else(sum(phase_complete_dbp) == 6, 1, 0),
         phase_complete_a1c = if_else(!is.na(hba1c), 1, 0),
         complete_case_a1c = if_else(sum(phase_complete_a1c) == 6, 1, 0),
         phase_complete_il1b = if_else(!is.na(il1b_dbs_a), 1, 0),
         complete_case_il1b = if_else(sum(phase_complete_il1b) == 6, 1, 0),
         phase_complete_il6 = if_else(!is.na(il6_dbs_a), 1, 0),
         complete_case_il6 = if_else(sum(phase_complete_il6) == 6, 1, 0),
         phase_complete_il8 = if_else(!is.na(il8_dbs_a), 1, 0),
         complete_case_il8 = if_else(sum(phase_complete_il8) == 6, 1, 0),
         phase_complete_tnfa = if_else(!is.na(tnfa_dbs_a), 1, 0),
         complete_case_tnfa = if_else(sum(phase_complete_tnfa) == 6, 1, 0),
         phase_complete_crp = if_else(!is.na(crp_dbs_a), 1, 0),
         complete_case_crp = if_else(sum(phase_complete_crp) == 6, 1, 0)) %>% 
  ungroup() %>% 
  select(-phase_complete_aix, -phase_complete_cpp, -phase_complete_sbp, -phase_complete_dbp,
         -phase_complete_a1c, -phase_complete_il1b, -phase_complete_il6, -phase_complete_il8,
         -phase_complete_tnfa, -phase_complete_crp)
  
##### Save as final combined dataset in chunk below #####
```

# Save final, combined dataset
```{r}
write_rds(new_vars, "output/r00_full_repeated_by_phase.rds")

write_csv(new_vars, "output/r00_full_repeated_by_phase.csv", na = " ")
```

# Change AIx/CPP outliers to NA and save dataset
```{r}
# load full dataset
r00_full_long <- read_rds("output/r00_full_repeated_by_phase.rds")

# USE THIS DATASET FOR AIx/CPP ANALYSES!!!
## Removes values >75 for AIx and CPP, and <-25 for AIx
## This dataset is already saved -- use code above to load
r00_model_data_outliers_removed <- r00_full_long %>% 
  # removes 6 potential "outliers" with high or low AIx
  # removes 4 potential "outliers" > 75mmHg CPP
  mutate(aug_index = if_else(aug_index > 75 | aug_index < -25, 9999, aug_index)) %>% 
  mutate(pulse_pressure_central = if_else(pulse_pressure_central > 75,
                                          9999, pulse_pressure_central)) %>% 
  replace_with_na(replace = list(aug_index = 9999)) %>% 
  replace_with_na(replace = list(pulse_pressure_central = 9999)) 
write_rds(r00_model_data_outliers_removed, "output/r00_model_data_outliers_removed.rds")
```



# Convert subsets of dataset back to wide
```{r}
spread_p <- r00_final_long %>% 
  select(house_id, phase, p_twa) %>% 
  spread(phase, p_twa) %>% 
  rename(p_twa_p1 = "1",
         p_twa_p2 = "2",
         p_twa_p3 = "3",
         p_twa_p4 = "4",
         p_twa_p5 = "5",
         p_twa_p6 = "6")

spread_a <- r00_final_long %>% 
  select(house_id, phase, a_twa) %>% 
  spread(phase, a_twa) %>% 
  rename(a_twa_p1 = "1",
         a_twa_p2 = "2",
         a_twa_p3 = "3",
         a_twa_p4 = "4",
         a_twa_p5 = "5",
         a_twa_p6 = "6")

bonnie_exposure <- full_join(spread_a, spread_p, by = "house_id")

write_csv(bonnie_exposure, "output/bonnie_exposure.csv", na = " ")
```



##### Convert Tim's Dataset from Wide to Long #####

```{r, message=FALSE}
# Load data
r00_full_wide <- read_xlsx("input/tim_28June2019.xlsx")
```


```{r}
tim_full_long <- r00_full_wide %>% 
  rename(beds_new_r00_p1 = beds_new) %>% 
  mutate(beds_new_r00_p2 = beds_new_r00_p1, 
         beds_new_r00_p3 = beds_new_r00_p1, 
         beds_new_r00_p4 = beds_new_r00_p1, 
         beds_new_r00_p5 = beds_new_r00_p1, 
         beds_new_r00_p6 = beds_new_r00_p1) %>%
  #transform data to long format with only 3 columns
  gather(key = "variable", value = "value", -house_id) %>% 
  #arrange data by house_id, descending
  arrange(house_id)

tim_full_repeated_by_phase <- tim_full_long %>%
  #separate variable to create new phase column
  separate(variable, c("variable", "phase"), sep = "_r00_p") %>%
  #replace "." with "99999" and then change to "na"
  mutate(value = if_else(value == ".", "99999", value)) %>% 
  replace_with_na(replace = list(value = 99999)) %>% 
  #separate phase and "new", then attach "new" to variable
  separate(phase, c("phase", "new"), sep = "_") %>% 
  unite("variable", c("variable", "new")) %>% 
  #remove NA from end of variables that was added above
  separate(variable, c("variable", "trash"), sep = "_NA") %>% 
  select(-"trash") %>% 
  #spread out into columns, grouped by house_id and phase
  spread(key = "variable", value = "value") %>% 
  arrange(house_id)

r00_sums_full_dataset <- readRDS("output/r00_sums_full_dataset.rds")

tim_joined <- tim_full_repeated_by_phase %>% 
  left_join(r00_sums_full_dataset, by = c("house_id", "phase"))

write_csv(tim_joined, "output/tim_data_28june2019.csv", na = " ")
```